---
title: "Prestige & Branding by Producers"
author: "Lauren Renaud"
date: "February, 2017"
output: 
  html_document:
    toc: true
    toc_depth: 4
---
```{r setup, echo=FALSE, include=FALSE, cache.lazy = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(knitr)

# without potency ----------
# first comparing price and producers without including THC / CBD numbers
# question to think about: should we try comparing something like price per THC instead
# of price? or is it ok to just compare on price, because higher THC is part of the 
# higher prestige aspect? Should try both. Initially doing without THC join

# first on inhalants only
inhalants <- readr::read_csv("../data/Dec2016/cleaned/samples/inhalants.csv")


```

# Product names by quantity sold

Top 25 product names by quantity sold. This uses a combination of productname and producer name from the inventory transfers to estimate individual products created by specific producers.

*Some `productname`s and some `trans_name`s are NA (more concerned about `trans_name`). Need to review further.*

```{r prod_quantsold_producer}
inhalants %>%
  filter(!is.na(inv_productname), !is.na(trans_name)) %>%
  group_by(inv_productname, trans_name) %>%
  summarise(num_sold = n()) %>%
  arrange(desc(num_sold)) %>%
  head(25) %>%
  kable(col.names=c("Product Name", "Producer Name", "Quantity Sold"))
```

# Distribution of price and quantity sold

Using the same combination of product name and producer name, this just looks at number sold and mean price for that product.

```{r hist_price_quantity}
inhalants %>%
  dplyr::filter(!is.na(inv_productname), !is.na(trans_name)) %>%
  dplyr::group_by(inv_productname, trans_name) %>%
  dplyr::summarise(
    num_sold = n(),
    median_price = median(retail_price)
    ) %>%
  filter(median_price < 250, num_sold < 50000,
         num_sold > 100, !is.na(inv_productname)) %>%
  ggplot(aes(x=median_price, y=num_sold)) +
  geom_point(alpha=0.5, color="darkslateblue") +
  labs(
    title = "Price and Quantity Sold, \nSales > 100, Median Price < $250",
    x= "Mean Retail Price by Product",
    y="Number of Product Sold"
  ) 

```


# Distribution of Prices by Producer

Looking at the mean, and median prices for a producer. This takes the mean for each product they sell, then takes the mean or median of those prices.

```{r hist_meanprice_meanproduct}
# histogram / density plot of mean retail prices
hist_median <- inhalants %>%
  dplyr::filter(!is.na(inv_productname), !is.na(trans_name)) %>%
  dplyr::group_by(trans_name, inv_productname) %>%
  dplyr::summarise(
    mean_retail = mean(retail_price, na.rm=T)
    #median_retail = median(retail_price, na.rm=T),
    #max_retail = max(retail_price, na.rm=T)#,
    # # transfer prices
    # mean_transsales = mean(trans_saleprice, na.rm=T),
    # median_transsales = median(trans_saleprice, na.rm=T),
    # max_transsales = max(trans_saleprice, na.rm=T),
    # mean_transunit = mean(trans_unitprice, na.rm=T),
    # median_transunit = median(trans_unitprice, na.rm=T),
    # max_transunit = max(trans_unitprice, na.rm=T)
  ) %>%
  dplyr::ungroup() %>% dplyr::group_by(trans_name) %>%
  dplyr::summarise(median_producer_retail = median(mean_retail)) %>%
  ggplot(aes(x=median_producer_retail)) +
  geom_density(alpha=0.5, fill="cadetblue3") +
  labs(
    title = "Median Sale Price \nDistribution",
    x= "Median Retail Price by Producer",
    y="Density"
  ) 

hist_mean <- inhalants %>%
  dplyr::filter(!is.na(inv_productname), !is.na(trans_name)) %>%
  dplyr::group_by(trans_name, inv_productname) %>%
  dplyr::summarise(
    mean_retail = mean(retail_price, na.rm=T)
    #median_retail = median(retail_price, na.rm=T),
    #max_retail = max(retail_price, na.rm=T)#,
    # # transfer prices
    # mean_transsales = mean(trans_saleprice, na.rm=T),
    # median_transsales = median(trans_saleprice, na.rm=T),
    # max_transsales = max(trans_saleprice, na.rm=T),
    # mean_transunit = mean(trans_unitprice, na.rm=T),
    # median_transunit = median(trans_unitprice, na.rm=T),
    # max_transunit = max(trans_unitprice, na.rm=T)
  ) %>%
  dplyr::ungroup() %>% dplyr::group_by(trans_name) %>%
  dplyr::summarise(mean_producer_retail = mean(mean_retail)) %>%
  ggplot(aes(x=mean_producer_retail)) +
  geom_density(alpha=0.5, fill="darkgreen") +
  labs(
    title = "Mean Sale Price \nDistribution",
    x= "Mean Retail Price by Producer",
    y="Density"
  ) 

grid.arrange(hist_median,hist_mean, ncol=2)
```

# Distribution of average price by products sold

We can also look at the relationship between mean or median price and number of products sold, but grouped on producer. This again finds the average price of each product, then finds the median price of products sold by a given producer to get their average price (x axis). Then finds the total number of items sold for a product, and takes median of that to get median products sold for each product that a producer creates.

```{r scatter_price_numsold}
# histogram / density plot of mean retail prices
inhalants %>%
  dplyr::group_by(trans_name, inv_productname) %>%
  dplyr::summarise(
    mean_retail = mean(retail_price, na.rm=T),
    num_sales = length(unique(dispensingid))
    #median_retail = median(retail_price, na.rm=T),
    #max_retail = max(retail_price, na.rm=T)#,
    # # transfer prices
    # mean_transsales = mean(trans_saleprice, na.rm=T),
    # median_transsales = median(trans_saleprice, na.rm=T),
    # max_transsales = max(trans_saleprice, na.rm=T),
    # mean_transunit = mean(trans_unitprice, na.rm=T),
    # median_transunit = median(trans_unitprice, na.rm=T),
    # max_transunit = max(trans_unitprice, na.rm=T)
  ) %>%
  dplyr::filter(num_sales < 1000000) %>%
  dplyr::ungroup() %>% dplyr::group_by(trans_name) %>%
  dplyr::summarise(median_prod_retail = median(mean_retail),
                   median_prod_sold = median(num_sales)) %>%
  ggplot(aes(x=median_prod_retail, y=median_prod_sold)) +
  geom_point(alpha=0.5, color="red4") +
  labs(
    title = "Sale Price & Quantity Sold",
    x= "Mean Retail Price by Product, Grouped by Producer",
    y="Median Products Sold, by Producer"
  ) 
```
  
  
```{r variance}
inventory.types <- read.csv("../data/Dec2016/cleaned/inventory_type.csv", sep=",", header=T)
potency <- readr::read_csv("../data/Dec2016/biotrackthc_labresults_potency_analysis.csv")
labsamples <- readr::read_csv("../data/Dec2016/biotrackthc_labresults_samples.csv")
potency_tidy <- potency %>%
  # was going to use tidyr to spread variable names
  # but some sample_ids have up to 15 tests
  # so summarizing first, assuming max() is most accurate
  # and that others might be missing values
  # but need to check
  dplyr::group_by(sample_id, name) %>%
  dplyr::summarise(value = max(value)) %>%
  # spread to get column each for THC, THCA, CBD, Total
  tidyr::spread(name, value) %>%
  # CBDA was a column of all null or 0
  dplyr::select(-(CBDA)) %>%
  dplyr::left_join(labsamples, by=c("sample_id" = "id")) %>%
  # select only variables for retail set
  # only including test_inventorytype and product name to confirm against inventory
  # but should be duplicative
  dplyr::select(sample_id, CBD, THC, THCA, Total, test_inventorytype = inventorytype,
                test_productname = product_name, inventoryparentid, strain) %>%
  dplyr::mutate(cbd_thc_ratio = CBD / THC) %>%
  dplyr::left_join(inventory.types, by=c("test_inventorytype"="inventorytype"))

# standard dev of potency & strain
potency_tidy %>%
  group_by(strain) %>%
  filter(!is.na(strain)) %>%
  summarise(
    meanTHC = mean(THC, na.rm=T),
    sdTHC = sd(THC, na.rm=T),
    meanCBD = mean(CBD, na.rm=T),
    sdCBD = sd(CBD, na.rm=T)
  ) %>%
  filter(sdTHC < 100, meanTHC < 100) %>%
  ggplot(aes(x=meanTHC, y=sdTHC)) +
  geom_point(alpha=0.5, color="olivedrab") +
  labs(
    title = "Variance in Strain Potency - All",
    x= "Mean THC by Strain Name",
    y="Standard Deviation THC by Strain Name"
  ) 

# mean log of standard deviation
logsd <- potency_tidy %>%
  group_by(strain) %>%
  filter(!is.na(strain)) %>%
  summarise(
    meanTHC = mean(THC, na.rm=T),
    sdTHClog = log(sd(THC, na.rm=T)),
    meanCBD = mean(CBD, na.rm=T),
    sdCBD = sd(CBD, na.rm=T)
  ) %>%
  filter(meanTHC < 100) %>%
  ggplot(aes(x=meanTHC, y=sdTHClog)) +
  geom_point(alpha=0.5, color="olivedrab") +
  labs(
    title = "Variance in Strain Potency - All",
    x= "Mean THC by Strain Name",
    y="Log of Std Dev THC by Strain Name"
  ) 

# number of diff product types by strain
logsdmean <- potency_tidy %>%
  group_by(strain) %>%
  filter(!is.na(strain)) %>%
  summarise(
    meanTHClog = log(mean(THC, na.rm=T)),
    sdTHClog = log(sd(THC, na.rm=T))#,
    #meanCBD = mean(CBD, na.rm=T),
    #sdCBD = sd(CBD, na.rm=T)
  ) %>%
  #filter(meanTHC < 100) %>%
  ggplot(aes(x=meanTHClog, y=sdTHClog)) +
  geom_point(alpha=0.5, color="olivedrab") +
  labs(
    title = "Variance in Strain Potency",
    x= "Log of Mean THC by Strain Name",
    y="Log of Std Dev THC by Strain Name"
  ) 

grid.arrange(logsd,logsdmean, ncol=2)

# by product type ----------
potency_tidy %>%
  group_by(strain, inv_type_name) %>%
  filter(!is.na(strain)) %>%
  summarise(
    meanTHC = mean(THC, na.rm=T),
    sdTHC = sd(THC, na.rm=T),
    meanCBD = mean(CBD, na.rm=T),
    sdCBD = sd(CBD, na.rm=T)
  ) %>%
  filter(sdTHC < 100, meanTHC < 100) %>%
  ggplot(aes(x=meanTHC, y=sdTHC)) +
  geom_point(alpha=0.5, color="seagreen4") +
  labs(
    title = "Variance in Strain Potency - All",
    x= "Mean THC by Strain Name",
    y="Standard Deviation THC by Strain Name"
  ) +
  facet_wrap("inv_type_name", ncol = 4) 

```
