---
title: "DD_Start_Day_of_Fall"
author: "Yutian Guo"
date: "April 3, 2017"
output: html_document
---


---
title: "Difference in Differences Pullman Clusten"
author: "Yutian Guo"
date: "March 3, 2017"
output: html_document
---



############ Library #################
```{r setup, include=FALSE}
library(ggplot2)
library(MASS)
library(caret)
library(knitr)
library(dplyr)
library(plyr)
library(data.table) 
library(reshape2)
library(lubridate) #date-time stuff
library(splines)
library(hexbin) #geom_hexbin
library(broom)
library(foreign)



```




############ Load Data ###############

```{r,cache=TRUE}
# pullman
pm <- read.csv("../data/NaturalExp_PM.csv",header = TRUE)
# Clarkston
ct <- read.csv("../data/NaturalExp_CT.csv",header = TRUE)
# Kittitas
#kitt<- read.csv("NaturalExp_KITT.csv",header = TRUE)
# Wallawalla
#walla <- read.csv("NaturalExp_WALLA.csv",header = TRUE)




```


Color Schema

```{r, include=FALSE }



# The palette with black:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# To use for fills, add
scale_fill_manual(values=cbPalette)

# To use for line and point colors, add
scale_colour_manual(values=cbPalette)

```


# Pre-Processing
```{r}
# Preprocessing

pm$date<-as.Date(pm$date)
ct$date<-as.Date(ct$date)
#kitt$date<-as.Date(kitt$date)
#walla$date<-as.Date(walla$date) 

# Add group number to two df; 0 - control group; 1 - experiment group
ct$treated <- rep(0,nrow(ct))
pm$treated <- rep(1,nrow(pm))
#kitt$treated<-rep(1,nrow(kitt))
#walla$treated<-rep(1,nrow(walla))

# Select useful columns

ct_selected<-ct%>%
  dplyr::select(date,trans,adj.daily.trans,revenue,
                adj.daily.revenue,perstore_dailytrans,
                perstore_dailyRev,adj.perstore.dailyRev,
                adj.perstore.dailytrans,treated)

pm_selected<-pm%>%
  dplyr::select(date,trans,adj.daily.trans,revenue,
                adj.daily.revenue,perstore_dailytrans, 
                perstore_dailyRev,adj.perstore.dailyRev, 
                adj.perstore.dailytrans,treated)

# kitt_selected<-kitt%>%
#   dplyr::select(date,trans,adj.daily.trans,revenue,
#                 adj.daily.revenue,perstore_dailytrans, 
#                 perstore_dailyRev,adj.perstore.dailyRev, 
#                 adj.perstore.dailytrans,treated)
# 
# walla_selected<-walla%>%
#   dplyr::select(date,trans,adj.daily.trans,revenue,
#                 adj.daily.revenue,perstore_dailytrans, 
#                 perstore_dailyRev,adj.perstore.dailyRev, 
#                 adj.perstore.dailytrans,treated)
```

# Control city : clarkston
num of store in ct is constantly 2 during this period



# Pullman
1. Population in Pullman: 31,682 (2014 census)
2. Washington State University (WSU) - 19,756 students at Pullman Campus
3. Stores:
   num of store in pm is 2 from 2016-3-1 to 2016-4-29, 3 from 2016-4-30 to 2016-7-19, 4 since 2016-7-20 


## Treatment 1 start of school (Monday, August 22, 2016)
```{r}
# end of spring : Friday, May 6, 2016
# The first day of instruction for the term.	Monday, August 22, 2016
# Final examinations end.	Friday, December 16, 2016


# Create a dummy variable when fall semester started.(Monday, August 22, 2016 )
ct_selected_2<-ct_selected
pm_selected_2<-pm_selected
ct_selected_2$T2_fallStart <-ifelse(ct_selected_2$date >= "2016-08-22", 1, 0)
pm_selected_2$T2_fallStart<-ifelse(pm_selected_2$date >= "2016-08-22", 1, 0)

# extract 2 month before and after 
pm_fall<-pm_selected_2[which(pm_selected_2$date>='2016-6-23'&pm_selected_2$date<'2016-10-22'),]
ct_fall<-ct_selected_2[which(ct_selected_2$date>='2016-6-23'&ct_selected_2$date<'2016-10-22'),]

# combine these two df into one
ct_pm_treat2<-rbind(ct_fall,pm_fall)






# Create an interaction between time and treated. We will call this interaction ??did??.
ct_pm_treat2$did_T2_fallStart = ct_pm_treat2$T2_fallStart * ct_pm_treat2$treated
```


## Pullman and Clarkston: Revenue and Transactions in Year 2016 


```{r}

ct2016 <- subset(ct_selected_2,date > '2016-1-1')
pm2016<- subset(pm_selected_2,date > '2016-1-1')
ct2016$rev_trans_ratio <- ct2016$adj.daily.revenue/ct2016$adj.daily.trans
pm2016$rev_trans_ratio <- pm2016$adj.daily.revenue/pm2016$adj.daily.trans

# "2015 - 2016?? Transactions: Clarkston vs Pullman"
ggplot()+
  geom_point(data=ct_selected_2,mapping = aes(x=date,y=trans),color ="#56B4E9" )+
  geom_smooth(data=ct_selected_2,mapping = aes(x=date,y=trans),method = 'lm',formula = y~ns(x, df=3),color = "#0072B2")+
  geom_point(data=pm_selected_2,mapping = aes(x=date,y=trans),color ="#F0E442" )+
  geom_smooth(data=pm_selected_2,mapping = aes(x=date,y=trans),method = 'lm',formula = y~ns(x, df=3),color =  "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2015 - 2016?? Transactions: Clarkston vs Pullman",
       x = 'Date', y = 'Daily total transactions')


# 2016 Transactions: Clarkston vs Pullman
ggplot()+
  geom_point(data=ct2016,mapping = aes(x=date,y=trans),color ="#56B4E9" )+
  geom_smooth(data=ct2016,mapping = aes(x=date,y=trans),method = 'lm',formula = y~ns(x, df=3),color = "#0072B2")+
  geom_point(data=pm2016,mapping = aes(x=date,y=trans),color ="#F0E442" )+
  geom_smooth(data=pm2016,mapping = aes(x=date,y=trans),method = 'lm',formula = y~ns(x, df=3),color =  "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2016 Transactions: Clarkston vs Pullman",
       x = 'Date', y = 'Daily total transactions')




#"2016 Transactions (Seasonal Adjusted): Clarkston vs Pullman"
ggplot()+
  geom_point(data=ct2016,mapping = aes(x=date,y=adj.daily.trans),color ="#56B4E9" )+
  # geom_smooth(data=ct2016,mapping = aes(x=date,y=adj.daily.trans),method = 'lm',formula = y~ns(x, df=3),color = "#0072B2")+
  geom_point(data=pm2016,mapping = aes(x=date,y=adj.daily.trans),color ="#F0E442" )+
  # geom_smooth(data=pm2016,mapping = aes(x=date,y=adj.daily.trans),
  #             method = 'lm',formula = y~ns(x, df=3),color =  "#CC79A7") +
  geom_smooth(data=subset(pm2016, date <= "2016-05-05"),mapping = aes(x=date,y=adj.daily.trans),
              method = 'lm',formula = y~ns(x, df=1),color =  "#CC79A7") +
  geom_smooth(data=subset(pm2016, date >= "2016-05-05" & date <= "2016-08-22"),
              mapping = aes(x=date,y=adj.daily.trans), 
              method = 'lm',formula = y~ns(x, df=1),color =  "#CC79A7") +
  geom_smooth(data=subset(pm2016, date >= "2016-08-22"),
              mapping = aes(x=date,y=adj.daily.trans), 
              method = 'lm',formula = y~ns(x, df=1),color =  "#CC79A7") +
  
  geom_smooth(data=subset(ct2016, date <= "2016-05-05"),mapping = aes(x=date,y=adj.daily.trans),
              method = 'lm',formula = y~ns(x, df=1),color =  "#0072B2") +
  geom_smooth(data=subset(ct2016, date >= "2016-05-05" & date <= "2016-08-22"),
              mapping = aes(x=date,y=adj.daily.trans), 
              method = 'lm',formula = y~ns(x, df=1),color =  "#0072B2") +
  geom_smooth(data=subset(ct2016, date >= "2016-08-22"),
              mapping = aes(x=date,y=adj.daily.trans), 
              method = 'lm',formula = y~ns(x, df=1),color =  "#0072B2") +
  
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2016 Transactions (Seasonal Adjusted): Clarkston vs Pullman",
       x = 'Date', y = 'Daily total transactions')

```



??
# Treatment 2 spring end
```{r}
# combine these two df into one
ct_pm_treat1<-rbind(ct_selected,pm_selected)

# Create a dummy variable to indicate the time when the treatment started.(Friday, May 6, 2016 as the experiment )
ct_pm_treat1$T1_springEnd <-ifelse(ct_pm_treat1$date >= "2016-05-06", 1, 0)


# extract 2 month before and after 
ct_pm_treat1<-ct_pm_treat1[which(ct_pm_treat1$date>='2016-3-1'&ct_pm_treat1$date<'2016-7-30'),]


# Create an interaction between time and treated. We will call this interaction ??did??.
ct_pm_treat1$did_T1_springEnd = ct_pm_treat1$T1_springEnd * ct_pm_treat1$treated


# 2016 'Spring and Summer Transactions(Seasonal Adjusted): pullman vs Clarkston'
ggplot(data = ct_pm_treat1,
       mapping= aes(x=date,y=adj.daily.trans,color= as.factor(treated),
                    linetype = as.factor(treated)))+
  geom_point()+
  # geom_smooth(method='lm', formula = y~ns(x, df=3))+
  geom_smooth(data=subset(ct_pm_treat1, date >= "2016-05-06"),
              mapping = aes(x=date,y=adj.daily.trans), 
              method = 'lm',formula = y~ns(x, df=1),color =  "#0072B2") +
  geom_smooth(data=subset(ct_pm_treat1, date <= "2016-05-06"),
              mapping = aes(x=date,y=adj.daily.trans), 
              method = 'lm',formula = y~ns(x, df=1),color =  "#0072B2") +
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  scale_linetype_discrete(name="City", 
                          breaks=c("0", "1"), 
                          labels = c("Clarkston", "Pullman"))+
   scale_colour_manual(values=cbPalette)+
  labs(title='Spring and Summer Transactions(Seasonal Adjusted): pullman vs Clarkston')



# DD Reg
didreg_adjTOTtrans_treat1 = lm(adj.daily.trans~treated+T1_springEnd+did_T1_springEnd, data = ct_pm_treat1)
summary(didreg_adjTOTtrans_treat1)


```


#######################################################
###y = total transaction,  Estimating the DID estimator 
#######################################################
```{r}
# view plot 
# Summer and Fall Transactions(Seasonal Adjusted): pullman vs Clarkston
ggplot(data = ct_pm_treat2,
       mapping= aes(x=date,y=adj.daily.trans,color= as.factor(treated),
                    linetype = as.factor(treated)))+
  geom_point()+
  geom_smooth(method='lm', formula = y~ns(x, df=3))+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  scale_linetype_discrete(name="City", 
                          breaks=c("0", "1"), 
                          labels = c("Clarkston", "Pullman"))+
   scale_colour_manual(values=cbPalette)+
  labs(title='Summer and Fall Transactions(Seasonal Adjusted): pullman vs Clarkston') 
    



# d-in-d regression
didreg_TOTtrans_treat2 = lm(trans~treated+T2_fallStart+did_T2_fallStart, data = ct_pm_treat2)
summary(didreg_TOTtrans_treat2)
# use seasonal adjusted
didreg_adjTOTtrans_treat2 = lm(adj.daily.trans~treated+T2_fallStart+did_T2_fallStart, data = ct_pm_treat2)
summary(didreg_adjTOTtrans_treat2)
```
________________________________________________________________________________________
conclusion:  *********************important
The coefficient for ??did_fall_start?? is the differences-in-differences estimator. The effect is significant at 0.000 level with the treatment having a positive effect.
________________________________________________________________________________________

## Conclusion Summary for Treatment 2
For treatment 2 fall_start, seasonal adjusted data performs better than not adjusted. And total data makes more sense than persotre data.
According to above results, the coefficient for ??did_fall_start?? is the differences-in-differences estimator. 
In terms of total transactions, The effect is significant at 0.000 level with the treatment having a positive effect.

lm(formula = adj.daily.trans ~ treated + T2_fallStart + did_T2_fallStart, 
    data = ct_pm_treat2)
                     Estimate    Std. Error t value Pr(>|t|)  
  did_T2_fallStart   316.91      49.95      6.344   6.79e-10 ***
  
 
 
 
Part II D-IN-D Regression By Product Type at Pullman City

Usable marijuana; extracts for inhalation; and edibles

```{r}

pm.pdct <- read.csv("NaturalExp_PM_product.csv", header = TRUE)
ct.pdct <- read.csv("NaturalExp_CT_product.csv", header = TRUE)

ct.pdct$treat <- rep(0, nrow(ct.pdct))
pm.pdct$treat <- rep(1, nrow(pm.pdct))

pm.pdct$date<-as.Date(pm.pdct$date)
ct.pdct$date<-as.Date(ct.pdct$date)

pm.pdct$edible <- rowSums(pm.pdct[,c("solid_edible", "liquid_edible")])
ct.pdct$edible <- rowSums(ct.pdct[,c("solid_edible", "liquid_edible")])

ct.pd2016<-subset(ct.pdct,date>'2016-1-1')
pm.pd2016<-subset(pm.pdct,date>'2016-1-1')

pm.4month<-pm.pd2016[which(pm.pd2016$date>='2016-6-22'&pm.pd2016$date<'2016-10-22'),]
ct.4month<-ct.pd2016[which(ct.pd2016$date>='2016-6-22'&ct.pd2016$date<'2016-10-22'),]
```

# Edible
```{r}

ggplot()+
  geom_point(data = ct.pd2016, mapping= aes(x=date,y=edible),color= "#56B4E9")+
  geom_smooth(data = ct.pd2016, mapping = aes(x=date,y=edible),
              method='lm', formula = y~ns(x, df=4),color = "#0072B2")+
  geom_point(data=pm.pd2016,mapping=aes(x=date,y=edible),color ="#F0E442")+
  geom_smooth(data=pm.pd2016, mapping = aes(x=date,y=edible),
              method='lm', formula = y~ns(x, df=4), color = "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Edible Transactions % : pullman vs Clarkston') 

ggplot()+
  geom_point(data = ct.4month, mapping= aes(x=date,y=edible),color= "#56B4E9")+
  geom_smooth(data = ct.4month, mapping = aes(x=date,y=edible),
              method='lm', formula = y~ns(x, df=4),color = "#0072B2")+
  geom_point(data=pm.4month,mapping=aes(x=date,y=edible),color ="#F0E442")+
  geom_smooth(data=pm.4month, mapping = aes(x=date,y=edible),
              method='lm', formula = y~ns(x, df=4), color = "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Edible Transactions % (Jun. - Oct.): pullman vs Clarkston') 
```



# Extract
```{r}

ggplot()+
  geom_point(data = ct.pd2016, mapping= aes(x=date,y=extract),color= "#56B4E9")+
  geom_smooth(data = ct.pd2016, mapping = aes(x=date,y=extract),
              method='lm', formula = y~ns(x, df=5),color = "#0072B2")+
  geom_point(data=pm.pd2016,mapping=aes(x=date,y=extract),color ="#F0E442")+
  geom_smooth(data=pm.pd2016, mapping = aes(x=date,y=extract),
              method='lm', formula = y~ns(x, df=5), color = "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Extract Transactions % : pullman vs Clarkston') 


ggplot()+
  geom_point(data = ct.4month, mapping= aes(x=date,y=extract),color= "#56B4E9")+
  geom_smooth(data = ct.4month, mapping = aes(x=date,y=extract),
              method='lm', formula = y~ns(x, df=3),color = "#0072B2")+
  geom_point(data=pm.4month,mapping=aes(x=date,y=extract),color ="#F0E442")+
  geom_smooth(data=pm.4month, mapping = aes(x=date,y=extract),
              method='lm', formula = y~ns(x, df=3), color = "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Extract Transactions % (Jun. - Oct.): pullman vs Clarkston') 
```


# Nicer Version of Product Mix

```{r}
# plot pullman

pmct.pdct <- rbind(pm.pdct[,c("date", "usable", "extract", "solid_edible", "liquid_edible", "treat")], ct.pdct[,c("date", "usable", "extract", "solid_edible", "liquid_edible", "treat")])
pmct.pdct$edible <- rowSums(pmct.pdct[,c("solid_edible", "liquid_edible")])

pmct.pdct.graph<-pmct.pdct%>%
  dplyr::select(1,2,3,7,6)%>%
  dplyr::filter(date>'2016-1-1')%>%
  tidyr::gather(usable,extract,edible, key = "Inv_Type", value = "Proportion")

pm.graph <- subset(pmct.pdct.graph,treat == 1)
ct.graph <- subset(pmct.pdct.graph,treat == 0)


pmct.pdct.graph2<-pmct.pdct%>%
  dplyr::select(1,3,7,6)%>%
  dplyr::filter(date>'2016-1-1')%>%
  tidyr::gather(extract,edible, key = "Inv_Type", value = "Proportion")

pm.graph2 <- subset(pmct.pdct.graph2,treat == 1)
ct.graph2 <- subset(pmct.pdct.graph2,treat == 0)

ggplot(data = pmct.pdct.graph, 
              mapping= aes(x=date,y=Proportion,color=Inv_Type,
                           linetype = as.factor(treat)))+
  geom_smooth(method='lm', formula = y~ns(x, df=3))+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  scale_linetype_discrete(name="City", 
                          breaks=c("0", "1"), 
                          labels = c("Clarkston", "Pullman"))+
   scale_colour_manual(values=cbPalette)+
    labs(title='Pullman vs Clarkston product mix 2016') 

ggplot(data = pmct.pdct.graph2, 
              mapping= aes(x=date,y=Proportion,color=Inv_Type,
                           linetype = as.factor(treat)))+
  geom_smooth(method='lm', formula = y~ns(x, df=3))+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  scale_linetype_discrete(name="City", 
                          breaks=c("0", "1"), 
                          labels = c("Clarkston", "Pullman"))+
   scale_colour_manual(values=cbPalette)+
    labs(title='Pullman vs Clarkston extract and edible ratio 2016') 

ggplot()+
  geom_smooth(data = ct.graph, mapping= aes(x=date,y=Proportion,color=Inv_Type),method='lm', formula = y~ns(x, df=10))+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Clarkston product mix 2016') 
```


############### may not need 
```{r}

ggplot(data = pm.graph2, mapping= aes(x=date,y=Proportion,color=Inv_Type))+
  geom_point()+
  geom_smooth(data = pm.graph2, mapping= aes(x=date,y=Proportion,color=Inv_Type),method='lm', formula = y~ns(x, df=4))+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Pullman product mix 2016') 

ggplot(data = ct.graph2, mapping= aes(x=date,y=Proportion,color=Inv_Type))+
  geom_point()+
  geom_smooth(data = pm.graph2, mapping= aes(x=date,y=Proportion,color=Inv_Type),method='lm', formula = y~ns(x, df=4))+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
    labs(title='Clarkston product mix 2016') 





```

 
  

##### Rev Graphs #####

```{r}
# Rev

ggplot()+
  geom_point(data=ct2016,mapping = aes(x=date,y=revenue),color ="#56B4E9" )+
  geom_smooth(data=ct2016,mapping = aes(x=date,y=revenue),method = 'lm',formula = y~ns(x, df=4),color = "#0072B2")+
  geom_point(data=pm2016,mapping = aes(x=date,y=revenue),color ="#F0E442" )+
  geom_smooth(data=pm2016,mapping = aes(x=date,y=revenue),method = 'lm',formula = y~ns(x, df=4),color =  "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2016 Revenue: Clarkston vs Pullman",x = 'Date', y = 'Daily total revenue')
```



```{r}
ggplot()+
  geom_point(data=ct2016,mapping = aes(x=date,y=adj.daily.revenue),color ="#56B4E9" )+
  geom_smooth(data=ct2016,mapping = aes(x=date,y=adj.daily.revenue),method = 'lm',formula = y~ns(x, df=4),color = "#0072B2")+
  geom_point(data=pm2016,mapping = aes(x=date,y=adj.daily.revenue),color ="#F0E442" )+
  geom_smooth(data=pm2016,mapping = aes(x=date,y=adj.daily.revenue),method = 'lm',formula = y~ns(x, df=4),color =  "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2016 Revenue (Seasonal Adjusted) : Clarkston vs Pullman",x = 'Date', y = 'Daily total revenue')
```



```{r}
ggplot()+
  geom_point(data=ct_selected_2,mapping = aes(x=date,y=adj.daily.revenue),color ="#56B4E9" )+
  geom_smooth(data=ct_selected_2,mapping = aes(x=date,y=adj.daily.revenue),method = 'lm',formula = y~ns(x, df=4),color = "#0072B2")+
  geom_point(data=pm_selected_2,mapping = aes(x=date,y=adj.daily.revenue),color ="#F0E442" )+
  geom_smooth(data=pm_selected_2,mapping = aes(x=date,y=adj.daily.revenue),method = 'lm',formula = y~ns(x, df=4),color =  "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2015-2016 Revenue (Seasonal Adjusted) : Clarkston vs Pullman",x = 'Date', y = 'Daily total revenue')


# Ratio

ggplot()+
  geom_point(data=ct2016,mapping = aes(x=date,y=rev_trans_ratio),color ="#56B4E9" )+
  geom_smooth(data=ct2016,mapping = aes(x=date,y=rev_trans_ratio),method = 'lm',formula = y~ns(x, df=4),color = "#0072B2")+
  geom_point(data=pm2016,mapping = aes(x=date,y=rev_trans_ratio),color ="#F0E442" )+
  geom_smooth(data=pm2016,mapping = aes(x=date,y=rev_trans_ratio),method = 'lm',formula = y~ns(x, df=4),color =  "#CC79A7")+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  labs(title="2016 Ratio (Seasonal Adjusted) : Clarkston vs Pullman",x = 'Date', y = 'Rev/trans')



```




########################################################
#y = total rev, Estimating the DID estimator 
#######################################################
```{r}
# view plot
ggplot(data = ct_pm_treat2,
       mapping= aes(x=date,y=adj.daily.revenue,color= as.factor(treated),
                    linetype = as.factor(treated)))+
  geom_point()+
  geom_smooth(method='lm', formula = y~ns(x, df=3))+
  geom_vline(xintercept= as.numeric(as.Date('2016-8-22')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  scale_linetype_discrete(name="City", 
                          breaks=c("0", "1"), 
                          labels = c("Clarkston", "Pullman"))+
   scale_colour_manual(values=cbPalette)+
  labs(title='Summer and Fall Revenue(Seasonal Adjusted): pullman vs Clarkston') 
    


ggplot(data = ct_pm_treat1,
       mapping= aes(x=date,y=adj.daily.revenue,color= as.factor(treated),
                    linetype = as.factor(treated)))+
  geom_point()+
  geom_smooth(method='lm', formula = y~ns(x, df=3))+
  geom_vline(xintercept= as.numeric(as.Date('2016-5-6')),linetype="dashed", size=1, colour="darkgreen")+
  geom_vline(xintercept= as.numeric(as.Date('2016-7-20')),linetype="dashed", size=1, colour="gray")+
  geom_vline(xintercept= as.numeric(as.Date('2016-4-30')),linetype="dashed", size=1, colour="gray")+
  scale_linetype_discrete(name="City", 
                          breaks=c("0", "1"), 
                          labels = c("Clarkston", "Pullman"))+
   scale_colour_manual(values=cbPalette)+
  labs(title='Spring and Summer Revenue(Seasonal Adjusted): pullman vs Clarkston') 

#
didreg_adjTOTRev_treat1 = lm(adj.daily.revenue~treated+T1_springEnd+did_T1_springEnd, data = ct_pm_treat1)
summary(didreg_adjTOTRev_treat1) 

# d-in-d regression
didreg_adjTOTRev_treat2 = lm(adj.daily.revenue~treated+T2_fallStart+did_T2_fallStart, data = ct_pm_treat2)
summary(didreg_adjTOTRev_treat2)
# use seasonal adjusted
didreg_adjTOTtrans_treat2 = lm(adj.daily.trans~treated+T2_fallStart+did_T2_fallStart, data = ct_pm_treat2)
summary(didreg_adjTOTtrans_treat2)


ggplot()+
  geom_point(data = ct_fall, mapping= aes(x=date,y=revenue),color= "#56B4E9")+
  geom_smooth(data = ct_fall, mapping = aes(x=date,y=revenue),
              method='lm', formula = y~ns(x, df=3),color = "#0072B2")+
  geom_point(data=pm_fall,mapping=aes(x=date,y=revenue),color ="#F0E442")+
  geom_smooth(data=pm_fall, mapping = aes(x=date,y=revenue),
              method='lm', formula = y~ns(x, df=3), color = "#CC79A7")+
    labs(title='Summer and Fall Revenue: pullman vs Clarkston') 


# d-in-d regression
didreg_TOTRev_treat2 = lm(revenue~treated+T2_fallStart+did_T2_fallStart, data = ct_pm_treat2)
summary(didreg_TOTRev_treat2) 


# use seasonal adjusted
didreg_adjTOTRev_treat2 = lm(adj.daily.revenue~treated+T2_fallStart+did_T2_fallStart, data = ct_pm_treat2)
summary(didreg_adjTOTRev_treat2) 

# seasonal adjusted are more significant than not adjusted
```




In terms of total revenues,The effect is significant at 0.01 level with the treatment having a positive effect.

lm(formula = adj.daily.revenue ~ treated + T2_fallStart + did_T2_fallStart, 
    data = ct_pm_treat2)
                     Estimate    Std. Error t value Pr(>|t|)      
  did_T2_fallStart   2251.4     1001.2   2.249   0.0251 *  



