---
title: "Classifying Extracts for Inhalation"
author: "Lauren Renaud"
date: "March, 2017"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(dplyr)
library(readr)
library(knitr)
library(tidyr)
options(scipen = 4)
```

```{r setup2, include=FALSE, cache=TRUE}

# pull in & clean dfs ------
# locatons
locations <- read.csv("../data/Dec2016/cleaned/locations/all_locations.csv", sep=",", header=T)
locations <- select(locations, location_id, name, city, loc_type = typesimp)

# inventory
inventory <- readr::read_csv("../data/Dec2016/biotrackthc_inventory.csv")
inventory$inv_date <- as.Date(as.POSIXct(inventory$sessiontime, 
                                            origin = "1970-01-01", tz="America/Los_Angeles"))
inventory$sample_id <- as.numeric(inventory$sample_id)
inventory$parentid <- as.numeric(inventory$parentid)
# join to inventory types
inventory.types <- read.csv("../data/Dec2016/cleaned/inventory_type.csv", sep=",", header=T)
inventory <- inventory %>%
  # get inventory types
  left_join(inventory.types, by="inventorytype") %>%
  # get location types
  left_join(locations, by=c("location" = "location_id")) %>%
  # drop other location variables
  select(-(name), -(city))
rm(inventory.types)

# selected variables
inv.select <- select(inventory, inventoryid = id, inv_strain = strain, parentid,
                     inv_type_name, inventoryparentid, productname, sample_id,
                     inv_location = location, inv_loctype = loc_type)

# dispensing
dispensing <- readr::read_csv("../data/Dec2016/biotrackthc_dispensing.csv")
dispensing <- filter(dispensing, inventorytype==24)
dispensing$saletime <- as.Date(as.POSIXct(dispensing$sessiontime, 
                                           origin = "1970-01-01", tz="America/Los_Angeles"))
dispens.select <- select(dispensing, dispensingid = id, retail_invid = inventoryid, retail_loc = location,
                         sale_price = price, saletime)
dispens.select <- dispens.select %>%
  left_join(locations, by=c("retail_loc" = "location_id")) %>%
  # drop other location variables
  select(-(name), -(city))


## testing going back one more step then looking at product types
inhalants.joined <- dispens.select %>%
  # first get to retailer's inventory to get `parentid`
  # as well as retail productname, retail strain
  dplyr::left_join(inv.select, by=c("retail_invid" = "inventoryid")) %>%
  # rename to inventory variables to clarify they are retail variables
  rename(retail_strain = inv_strain, retail_parentid = parentid, retail_invtype = inv_type_name,
         retail_invparentid = inventoryparentid, retail_prodname = productname, retail_sampId = sample_id,
         retail_location = inv_location) %>%
  # then use retailer's parentid to get to processor's inventoryid
  left_join(inv.select, by=c("retail_parentid" = "inventoryid")) %>%
  # then rename processor inventory variables
  rename(process_strain = inv_strain, process_parentid = parentid,
         process_invparentid = inventoryparentid, process_invtype = inv_type_name,
         process_prodname = productname, process_sampleid = sample_id, process_loc = inv_location) %>%
  # then use processors's parentid to get to one step further back inventoryid
  # these variables will now be called "inv_variablename"
  left_join(inv.select, by=c("process_invparentid" = "inventoryid"))


# 5% of product names for inhalants are missing, which is ~ the same as in full inventory df
# sum(is.na(inventory$productname[inventory$inventorytype==24])) / sum(inventory$inventorytype==24)
# # 33% are missing for processors' product name
# sum(is.na(inhalants.joined$inv_prodname)) / nrow(inhalants.joined)
# # inventory type
# # missing for 70 of joined inhalants (out of 6 million)
# sum(is.na(inhalants.joined$retail_invtype)) / nrow(inhalants.joined)
# 
# dispeningtypes <- unique(dispensing$inventorytype[!is.na(dispensing$inventorytype)])


# first get list/df of inhalantnames
inhalantnames <- as.data.frame(unique(inhalants.joined$retail_prodname))
# rename column so we can call it
colnames(inhalantnames) <- "retail_prodname"

# get a df that is for each unique inhalant name, the boolean values for categorizing
inhalantnames <- inhalantnames %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    cartidge = grepl("cart|vap|vc|pen|refill", retail_prodname, ignore.case = T),
    oil = grepl("oil", retail_prodname, ignore.case = T),
    BHO = grepl("BHO|butane", retail_prodname, ignore.case = T),
    hash = grepl("hash", retail_prodname, ignore.case = T),
    kief = grepl("kief|keif", retail_prodname, ignore.case = T),
    bubble = grepl("bubble", retail_prodname, ignore.case = T),
    shatter = grepl("shatter", retail_prodname, ignore.case = T),
    dab = grepl("dab", retail_prodname, ignore.case = T),
    resin = grepl("resin", retail_prodname, ignore.case = T),
    wax = grepl("wax", retail_prodname, ignore.case = T),
    uncategorized = (!cartidge & !oil & !BHO & !kief & !bubble & !shatter & !dab & !resin & !wax)
  )

# join classified inhalantnames back to dispening df
inhalants.joined$retail_prodname <- as.factor(inhalants.joined$retail_prodname)
inhalants <- left_join(inhalants.joined, inhalantnames, by="retail_prodname")

prelimCat <- inhalants %>%
  dplyr::select(dispensingid, cartidge:uncategorized) %>%
  tidyr::gather(keyword, status, cartidge:uncategorized) %>%
  dplyr::group_by(keyword) %>%
  dplyr::summarise(perc = round(sum(status==TRUE) / nrow(inhalants)*100,1),
                   count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc))

# trying to get count of how many products hit more than category
# doing just based on names, not actual number of products
# because full df was long to run, but could check again later
num.keywords <- inhalantnames %>%
  tidyr::gather(keyword, status, cartidge:uncategorized) %>%
  dplyr::group_by(retail_prodname) %>%
  dplyr::summarise(numCat = sum(status==TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(numCat) %>%
  dplyr::summarise(distro_numkeywords = n(),
                   perc_numkeywords = n() / nrow(inhalantnames))

```


# Key findings

 - Able to perform some form of **classification for about `r round(sum(!inhalants$uncategorized) / nrow(inhalants)*100,0)`%** of the products for inhalation in the dispensing file.
 - Including processors' inventory types in the process should get the number of **unclassified inhalants down to about 16%**.
 - Need to review these preliminary categories from a domain standpoint, and to consider purposes of classification.
 - May need stricter categorization for about `r round(sum(num.keywords$distro_numkeywords[num.keywords$numCat>1]) / nrow(inhalantnames)*100,0)`% of products that match more than one keyword. 


# Initial classification

Our first pass at categorizing inhalants is by searching product names for what would indicate product types. This method is able to classify `r round(sum(!inhalants$uncategorized) / nrow(inhalants)*100,1)`% of the products for inhalation in the dispensing file, which is `r round(sum(!inhalantnames$uncategorized) / nrow(inhalantnames)*100,1)`% of inhalant product names.

This table shows how many products fit each classification as well as the strings used for classificiation. (For "hash", it also picks up "hashish", but hashish was not searched for separately.) These do not sum to 100% because `r round(sum(num.keywords$distro_numkeywords[num.keywords$numCat>1]) / nrow(inhalantnames)*100,1)`% of product names contain more than one string.

```{r prelimcat_table, warning=FALSE}

# add a column of strings used for categorization
category.strings <- read.csv("../data/Dec2016/cleaned/testing/categoryStrings.csv", sep=",", header=T)
prelimCat_labels <- prelimCat %>%
  dplyr::left_join(category.strings, by="keyword")

# reorder the new columsns
refcols <- c("string", "keyword", "perc", "count")
prelimCat_labels <- prelimCat_labels[, c(refcols, setdiff(names(prelimCat_labels), refcols))]

# output table
knitr::kable(prelimCat_labels, col.names = c("Search String", "Keyword", "Percent", "Count"),
             # make all columns right aligned so it's easier to see keyword near percent value
               align=c("r", "r", "r", "r"))
```

While we could do a more thorough analysis of all the overlapping keywords, we can first look at "cartridges" and "oil" first to see what these look like.

### Overlap: Cartridges

```{r prelimcat_cartridges, warning=FALSE}
# take inhalants dataframe
overlap.cart <- inhalants %>%
  # limit to only cartridges
  filter(cartidge) %>%
  # get a total count of number of cartridges
  dplyr::mutate(cart_count = n()) %>%
  # select that count, row identifier, and then catetories other than cartridge
  dplyr::select(cart_count, dispensingid, BHO:uncategorized) %>%
  # use gather to get dispensingid + one colum for keyword + one colum for true or false
  tidyr::gather(keyword, status, BHO:uncategorized) %>%
  # group on keyword to get statistics for each keyword
  dplyr::group_by(keyword) %>%
  dplyr::summarise(
    # percent of all inhalant products that match that classification
    perc.inhalants = round(sum(status==TRUE) / nrow(inhalants)*100,2),
    # percent of cartridges that match that classification
    # using cart_count[1] because there are many cart_count's, even though they all have
    # the same value, need to tell it to just take the first one
    perc.cart = round(sum(status==TRUE) / cart_count[1] * 100,2),
    # count of that classification within cartridges
    count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc.cart))

```

In a cursory look at the product names, it looked like things that are categorized as "cartridges" might be picking up other keywords too. This table looks only at things that are cartridges, and then what other, additional keywords they also pick up, as well as their pecent of all inhalants in the market, and percentage of cartridges in the market.

Overall `r sum(overlap.cart$perc.cart)`% of cartidges are picking up other keywords, with the highest being butane hash oil at `r sum(overlap.cart$perc.cart[overlap.cart$keyword=="BHO"])`% of the cartridges. We will have to consider whether to categorize as "cartridge" first, or as BHO, or as something like "BHO cartridge", and similarly but less pressing with other subcategories of cartridges.

```{r, prelimcat_cartridges2, warning=FALSE}
knitr::kable(overlap.cart, col.names = c("Keyword", "% of Inhalants", "% of Cartidges", "Count"),
               align=c("r", "r", "r", "r"))
```

### Overlap: Oil

```{r prelimcat_oil, warning=FALSE}

overlap.oil <- inhalants %>%
  # keep only oils
  dplyr::filter(oil) %>%
  # get count of number of oils in df
  dplyr::mutate(oil_count = n()) %>%
  # select only that count of rows in this filtered dataframe,
  # row identifier, and classifications other than oil
  dplyr::select(oil_count, dispensingid, cartidge, BHO:uncategorized) %>%
  # gather to get row identified + column of keywords + column of T/F values
  tidyr::gather(keyword, status, cartidge, BHO:uncategorized) %>%
  # group by keyword to get statistics for each keyword
  dplyr::group_by(keyword) %>%
  dplyr::summarise(
    # percent of all inhalants that are this keyword
    perc.inhalants = round(sum(status==TRUE) / nrow(inhalants)*100,2),
    # percent of oil category that are also this keyword
    # using oil_count[1] because there are many oil_count's, even though they all have
    # the same value, need to tell it to just take the first one
    perc.oil = round(sum(status==TRUE) / oil_count[1] * 100,2),
    # count of this category within oils
    count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc.oil))

```

It also looks like things that are categorized as "oil" might be picking up other keywords too. This table looks only at things that are oil, and then what other, additional keywords they also pick up, their pecent of all inhalants in the market, and percentage of oils in the market.

It appears that `r sum(overlap.oil$perc.oil[overlap.oil$keyword=="cartidge"])`% of the oils are also listed as cartridges, which makes sense. It might be best to categorize as "cartridge" first, and "oil" if not a cartridge. Also `r sum(overlap.oil$perc.oil[!overlap.oil$keyword=="cartidge"])`% of "oils" are also picking up other keywords, which is something we could explore further to determine how to categorize.

```{r prelimcat_oil2, warning=FALSE}
knitr::kable(overlap.oil, col.names = c("Keyword", "% of Inhalants", "% of Oils", "Count"),
               align=c("r", "r", "r", "r"))
```

# Processor Types

A way to possibly double check our above classifications, and to attempt to classify those that were "uncategorized", is to look at the inventory types for the processors.

For about half of the inhalants, the processor also listed the product type as "Marijuana Extract for Inhalation", but for the other half, we have more detail about what went into the product. It also may be possible, if needed or useful, to try to go back one further step in the suppy chain to see what inventory types came before "Extract for Inhalation".

```{r processortypes, warning=FALSE}
# combinations of inventory types
process.types <- inhalants %>%
  # for some reason there is a very small number that are missing retail inventory type
  # that didn't wokr in the join correctly
  # screening these 70 out, but might investigate why
  filter(!is.na(retail_invtype)) %>%
  # group by processor's inventory type to get count and stats of the combinations
  group_by(process_invtype) %>%
  summarise(perc = round( n() / nrow(inhalants.joined)*100,1),
            count = n()) %>%
  arrange(desc(count))

knitr::kable(process.types, col.names = c("Processor's Inventory Type - All Inhalants",
                                          "Percent of Inhalants",
                                          "Count"),
               align=c("r", "r", "r"))


process.types.uncategorized <- inhalants %>%
  # same as above, but restricted to inhalants that are uncategorized
  filter(!is.na(retail_invtype), uncategorized) %>%
  # get count of number of uncategorized
  mutate(total = n()) %>%
  group_by(process_invtype) %>%
  summarise(perc = round(n() / total[1] *100,1),
            count = n()) %>%
  arrange(desc(count))

```

More excitingly, we should be able to classify an additional `r round(sum(process.types.uncategorized$perc[process.types.uncategorized$process_invtype!="Marijuana Extract for Inhalation" & process.types.uncategorized$process_invtype!="Food Grade Solvent Extract" & !is.na(process.types.uncategorized$process_invtype)]),1)`% of the inhalants that we were not able to categorized by product name and keywords by looking at the processor's listed inventory types. This should allow us to get our uncategorized products down to about `r round(sum(inhalants$uncategorized, na.rm=T) / nrow(inhalants) * (sum(process.types.uncategorized$perc[process.types.uncategorized$process_invtype!="Marijuana Extract for Inhalation" & process.types.uncategorized$process_invtype!="Food Grade Solvent Extract"], na.rm=T)/100)*100,1)`% of inhalants.

```{r processortypes2, warning=FALSE}

knitr::kable(process.types.uncategorized, col.names = c("Processor's Inventory Type",
                                                        "Percent of Uncategorized",
                                                        "Count"),
             align=c("r", "r", "r"))

```

# Next Steps

 - Explore the still uncategorized inhalants to see if they have any time, price, potency, etc trends
 - Explore the `r round(sum(num.keywords$distro_numkeywords[num.keywords$numCat>1]) / nrow(inhalantnames)*100,1)`% of overlapping keyword classifications and determine how to categorize them
 - Possibly aggregage back up into more generalized inhalant categories like "cartidge", "dab / wax / shatter", "other", or something else that more generally captures either use-type, potency cluster, or both
 - Scatterplot of existing categories, possible cluster model, which may also help classify the uncategorized


# Data cleaning and error checking

I noticed a few oddities while working through the data that are worth noting for future work and cleaning.

First, there are three instances in the dispensing (aka retail) table where the location type is not a retailer. They all have negative sale prices, so I'm thinking someone coded refunds as going back to the Processor or Producer-Processor.

```{r nonretailers}
# testing location types in dispensing file ------
# there are two processors and one producer-processor who show up in the dispensing df
# but each one only shows up once
# and they're for negative sale_price so maybe refunds?
#table(dispens.select$loc_type)
#sum(dispens.select$loc_type=="Processor" | dispens.select$loc_type=="Producer-Processor")
nonretailers <- dplyr::filter(dispens.select, loc_type=="Processor" | loc_type=="Producer-Processor")
knitr::kable(nonretailers, col.names = c("dispensingid", "retail invid", "retail loc", "sale price",
                                         "sale time", "inv loc type"))
```


```{r combos1}
# testing that retail locations match retail inventory locations -------
# building df that's only dispensing locations and inventory locations
test.retaillocations <- dispens.select %>%
  # first get retailers
  dplyr::filter(loc_type=="Retailer") %>%
  # and their locations
  dplyr::left_join(locations, by=c("retail_loc" = "location_id")) %>%
  # keep only variables we need for this comparison
  dplyr::select(dis_loc = retail_loc, dis_name = name, dis_city = city, dis_loctype = loc_type.x,
                retail_invid, -(sale_price), -(saletime)) %>%
  # get to the retail item's inventory
  dplyr::left_join(inv.select, by=c("retail_invid" = "inventoryid")) %>%
  # select those location variables
  dplyr::select(dis_loc, dis_name, dis_city, dis_loctype, retail_invid, inv_location) %>%
  left_join(locations, by=c("inv_location" = "location_id")) 

# then for each retail location, getting how many inventory locations are associated with it
# and percent of their entries for each
test.combos <- test.retaillocations %>%
  # group by the dispending location
  dplyr::group_by(dis_loc) %>%
  # get number of times that dispending location shows up
  dplyr::mutate(dis_count = n()) %>%
  dplyr::ungroup() %>%
  # now group for each pair of dispening location and inventory locations
  # and get those stats and counts
  dplyr::group_by(dis_loc, inv_location) %>%
  dplyr::summarise(combocount = n(),
            comboperc = round(n() / dis_count[1]*100,1),
            dis_city = dis_city[1],
            inv_city = city[1],
            inv_loctype = loc_type[1]) #%>%
  #dplyr::arrange(dis_loc, comboperc)
#hist(test.combos$comboperc)
#sum(test.combos$combocount[test.combos$combocount < 98]) / nrow(test.retaillocations)

# find average number of combinations
avg.combos <- test.combos %>%
  dplyr::group_by(dis_loc) %>%
  dplyr::summarise(count=n()) %>%
  dplyr::ungroup() %>%
  dplyr::summarise(avg.combos = median(count, na.rm=T))
```

I also noticed that in `r round(sum(test.combos$combocount[test.combos$combocount < 97]) / nrow(test.retaillocations)*100,1)`% of dispensing rows, when you link back to the inventory file, the inventory location does not match the retailer's location.

While this is a small portion of the overall dispensing and inventory, the median number of different inventory locations listed for each retail location is `r round(avg.combos$avg.combos,1)`, which includes those that only have one inventory location listed.

This displays a sample of what these combinations look like.

```{r combos2}
# display head for report
head(test.combos, 15) %>%
  knitr::kable(col.names=c("Dispense Loc", "Inv Loc", "Count",
                           "Percent", "Dispense City", "Inv City",
                           "Inv Location Type"))
```

Lastly, `productname` is missing for `r round(sum(is.na(inhalants.joined$retail_prodname)) / nrow(inhalants.joined)*100,1)`% of inhalants. This is compared to an estimated 6% of retail products of all types that are missing product names.

```{r other, warning=FALSE}
# Future code for exploring relationship of potency
# # labs -------
# potency <- readr::read_csv("../data/Dec2016/biotrackthc_labresults_potency_analysis.csv")
# labsamples <- readr::read_csv("../data/Dec2016/biotrackthc_labresults_samples.csv")
# labsamples$inventoryid <- as.numeric(labsamples$inventoryid)
# potency_tidy <- potency %>%
#   # was going to use tidyr to spread variable names but some sample_ids have up to 15 tests
#   # so summarizing first, assuming max() is most accurate and that others might be missing
#   # values but need to check
#   dplyr::group_by(sample_id, name) %>%
#   dplyr::summarise(value = max(value)) %>%
#   # spread to get column each for THC, THCA, CBD, Total
#   tidyr::spread(name, value) %>%
#   # CBDA was a column of all null or 0
#   dplyr::select(-(CBDA)) %>%
#   dplyr::left_join(labsamples, by=c("sample_id" = "id")) %>%
#   # select only variables for retail set
#   # only including test_inventorytype and product name to confirm against inventory
#   # but should be duplicative
#   dplyr::select(sample_id, CBD, THC, THCA, Total, test_inventorytype = inventorytype,
#                 test_productname = product_name, inventoryid, inventoryparentid)




# 

# 
# 
# resources <- resources %>%
#   dplyr::rowwise() %>%
#   dplyr::mutate(
#     cartidge = grepl("cart|vap|vc|pen|refill", productname, ignore.case = T),
#     inhalType = ifelse(grepl("oil", productname), "Oil",
#                        ifelse(grepl("BHO", productname), "BHO",
#                               ifelse(grepl())))
#     
# )
```



