---
title: "Classifying Extracts for Inhalation"
author: "Lauren Renaud"
date: "March, 2017"
output:
  html_document:
    toc: yes
    toc_depth: 4
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(dplyr)
library(readr)
library(knitr)
library(tidyr)
options(scipen = 4)
```

```{r setup2, include=FALSE, cache=TRUE}

# pull in & clean dfs ------
# locatons
locations <- read.csv("../data/Dec2016/cleaned/locations/all_locations.csv", sep=",", header=T)
locations <- select(locations, location_id, name, city, loc_type = typesimp)

# inventory
inventory <- readr::read_csv("../data/Dec2016/biotrackthc_inventory.csv")
inventory$inv_date <- as.Date(as.POSIXct(inventory$sessiontime, 
                                            origin = "1970-01-01", tz="America/Los_Angeles"))
inventory$sample_id <- as.numeric(inventory$sample_id)
inventory$parentid <- as.numeric(inventory$parentid)
# join to inventory types
inventory.types <- read.csv("../data/Dec2016/cleaned/inventory_type.csv", sep=",", header=T)
inventory <- inventory %>%
  # get inventory types
  left_join(inventory.types, by="inventorytype") %>%
  # get location types
  left_join(locations, by=c("location" = "location_id")) %>%
  # drop other location variables
  select(-(name), -(city))
rm(inventory.types)

# selected variables
inv.select <- select(inventory, inventoryid = id, inv_strain = strain, parentid,
                     inv_type_name, inventoryparentid, productname, sample_id,
                     inv_location = location, inv_loctype = loc_type)

# dispensing
dispensing <- readr::read_csv("../data/Dec2016/biotrackthc_dispensing.csv")
dispensing <- filter(dispensing, inventorytype==24)
dispensing$saletime <- as.Date(as.POSIXct(dispensing$sessiontime, 
                                           origin = "1970-01-01", tz="America/Los_Angeles"))
dispens.select <- select(dispensing, dispensingid = id, retail_invid = inventoryid, retail_loc = location,
                         sale_price = price, saletime)
dispens.select <- dispens.select %>%
  left_join(locations, by=c("retail_loc" = "location_id")) %>%
  # drop other location variables
  select(-(name), -(city))


## testing going back one more step then looking at product types
inhalants.joined <- dispens.select %>%
  # first get to retailer's inventory to get `parentid`
  # as well as retail productname, retail strain
  dplyr::left_join(inv.select, by=c("retail_invid" = "inventoryid")) %>%
  # rename to inventory variables to clarify they are retail variables
  rename(retail_strain = inv_strain, retail_parentid = parentid, retail_invtype = inv_type_name,
         retail_invparentid = inventoryparentid, retail_prodname = productname, retail_sampId = sample_id,
         retail_location = inv_location) %>%
  # then use retailer's parentid to get to processor's inventoryid
  left_join(inv.select, by=c("retail_parentid" = "inventoryid")) %>%
  # then rename processor inventory variables
  rename(process_strain = inv_strain, process_parentid = parentid,
         process_invparentid = inventoryparentid, process_invtype = inv_type_name,
         process_prodname = productname, process_sampleid = sample_id, process_loc = inv_location) %>%
  # then use processors's parentid to get to one step further back inventoryid
  # these variables will now be called "inv_variablename"
  left_join(inv.select, by=c("process_invparentid" = "inventoryid"))


# 5% of product names for inhalants are missing, which is ~ the same as in full inventory df
# sum(is.na(inventory$productname[inventory$inventorytype==24])) / sum(inventory$inventorytype==24)
# # 33% are missing for processors' product name
# sum(is.na(inhalants.joined$inv_prodname)) / nrow(inhalants.joined)
# # inventory type
# # missing for 70 of joined inhalants (out of 6 million)
# sum(is.na(inhalants.joined$retail_invtype)) / nrow(inhalants.joined)
# 
# dispeningtypes <- unique(dispensing$inventorytype[!is.na(dispensing$inventorytype)])


# first get list/df of inhalantnames
inhalantnames <- as.data.frame(unique(inhalants.joined$retail_prodname))
# rename column so we can call it
colnames(inhalantnames) <- "retail_prodname"

# get a df that is for each unique inhalant name, the boolean values for categorizing
inhalantnames <- inhalantnames %>%
  dplyr::rowwise() %>%
                 # boolean for cartridge
  dplyr::mutate(cartridge = grepl("cart|vap|vc|pen|refill", retail_prodname, ignore.case = T),
                # categorical
                type = ifelse(
                  grepl("BHO|butane", retail_prodname, ignore.case = T), "BHO",
                  ifelse(grepl("CO2", retail_prodname, ignore.case = T), "CO2",
                         ifelse(grepl("hash", retail_prodname, ignore.case = T), "hash",
                                ifelse(grepl("hash", retail_prodname, ignore.case = T), "kief",
                                       ifelse(grepl("bubble", retail_prodname, ignore.case = T), "bubble",
                                              ifelse(grepl("shatter", retail_prodname, ignore.case = T), "shatter",
                                                     ifelse(grepl("dab", retail_prodname, ignore.case = T), "dab",
                                                            ifelse(grepl("resin", retail_prodname, ignore.case = T), "resin",
                                                                   ifelse(grepl("wax", retail_prodname, ignore.case = T), "wax",
                                                                          "other"))))))))
                ),
                # now booleans for each
                oil = grepl("oil", retail_prodname, ignore.case = T),
                CO2 = grepl("CO2", retail_prodname, ignore.case=T),
                BHO = grepl("BHO|butane", retail_prodname, ignore.case = T),
                hash = grepl("hash", retail_prodname, ignore.case = T),
                kief = grepl("kief|keif", retail_prodname, ignore.case = T),
                bubble = grepl("bubble", retail_prodname, ignore.case = T),
                shatter = grepl("shatter", retail_prodname, ignore.case = T),
                dab = grepl("dab", retail_prodname, ignore.case = T),
                resin = grepl("resin", retail_prodname, ignore.case = T),
                wax = grepl("wax", retail_prodname, ignore.case = T),
                uncategorized = (!cartridge & !CO2 & !oil & !BHO & !kief & !bubble & !shatter & !dab & !resin & !wax),
                uncat_notcart = (!CO2 & !oil & !BHO & !kief & !bubble & !shatter & !dab & !resin & !wax)
  )

# join classified inhalantnames back to dispening df
inhalants.joined$retail_prodname <- as.factor(inhalants.joined$retail_prodname)
inhalants <- left_join(inhalants.joined, inhalantnames, by="retail_prodname")

prelimCat <- inhalants %>%
  dplyr::select(dispensingid, cartridge:uncategorized) %>%
  tidyr::gather(keyword, status, cartridge:uncategorized) %>%
  dplyr::group_by(keyword) %>%
  dplyr::summarise(perc = round(sum(status==TRUE) / nrow(inhalants)*100,1),
                   count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc))

# trying to get count of how many products hit more than category
# doing just based on names, not actual number of products
# because full df was long to run, but could check again later
num.keywords <- inhalantnames %>%
  tidyr::gather(keyword, status, cartridge:uncategorized) %>%
  dplyr::group_by(retail_prodname) %>%
  dplyr::summarise(numCat = sum(status==TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(numCat) %>%
  dplyr::summarise(distro_numkeywords = n(),
                   perc_numkeywords = n() / nrow(inhalantnames))

```


# Key findings

 - Able to perform some form of **classification for about `r round(sum(!inhalants$uncategorized) / nrow(inhalants)*100,0)`%** of the products for inhalation in the dispensing file (counted by number of items sold in the dispensing file).
 - Need to review these preliminary categories from a domain standpoint, and to consider purposes of classification.
 - May need stricter categorization for about `r round(sum(num.keywords$distro_numkeywords[num.keywords$numCat>1]) / nrow(inhalantnames)*100,0)`% of products sold that match more than one keyword. 


# Initial classification: Keyword Search

Our first pass at categorizing inhalants is by searching product names for what would indicate product types. This method is able to classify `r round(sum(!inhalants$uncategorized) / nrow(inhalants)*100,1)`% of "Marijuana Extract for Inhalation" products that were sold in the dispensing file, which is `r round(sum(!inhalantnames$uncategorized) / nrow(inhalantnames)*100,1)`% of inhalant product names.

This table shows how many products fit each classification as well as the strings used for classificiation. (For "hash", it also picks up "hashish", but hashish was not searched for separately.) These do not sum to 100% because `r round(sum(num.keywords$distro_numkeywords[num.keywords$numCat>1]) / nrow(inhalantnames)*100,1)`% of product names contain more than one string. `Count` here is counting number of products appearing in the dispensing (retail) file, not a count of product names.

While we could do a more thorough analysis of all the overlapping keywords, for this preliminary pass below we can look at "cartridges" and "oil" to see what the overlap for these keywords look like.

```{r prelimcat_table, warning=FALSE}

# add a column of strings used for categorization
category.strings <- read.csv("../data/Dec2016/cleaned/testing/categoryStrings.csv", sep=",", header=T)
prelimCat_labels <- prelimCat %>%
  dplyr::left_join(category.strings, by="keyword")

# reorder the new columsns
refcols <- c("string", "keyword", "perc", "count")
prelimCat_labels <- prelimCat_labels[, c(refcols, setdiff(names(prelimCat_labels), refcols))]

# output table
knitr::kable(prelimCat_labels, col.names = c("Search String", "Keyword", "Percent", "Count"),
             # make all columns right aligned so it's easier to see keyword near percent value
               align=c("r", "r", "r", "r"))

```


### Overlap: Cartridges

```{r prelimcat_cartridges, warning=FALSE}
# take inhalants dataframe
overlap.cart <- inhalants %>%
  # limit to only cartridges
  filter(cartridge) %>%
  # get a total count of number of cartridges
  dplyr::mutate(cart_count = n()) %>%
  # select that count, row identifier, and then catetories other than cartridge
  dplyr::select(cart_count, dispensingid, oil:wax) %>%
  # use gather to get dispensingid + one colum for keyword + one colum for true or false
  tidyr::gather(keyword, status, oil:wax) %>%
  # group on keyword to get statistics for each keyword
  dplyr::group_by(keyword) %>%
  dplyr::summarise(
    # percent of all inhalant products that match that classification
    perc.inhalants = round(sum(status==TRUE) / nrow(inhalants)*100,2),
    # percent of cartridges that match that classification
    # using cart_count[1] because there are many cart_count's, even though they all have
    # the same value, need to tell it to just take the first one
    perc.cart = round(sum(status==TRUE) / cart_count[1] * 100,2),
    # count of that classification within cartridges
    count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc.cart))

```

In a cursory look at the product names, it looked like things that are categorized as "cartridges" might be picking up other keywords too. This table looks only at things that are cartridges, and then what other, additional keywords they also pick up, as well as their pecent of all inhalants in the market, and percentage of cartridges in the market.

Overall `r sum(overlap.cart$perc.cart)`% of cartridges are picking up other keywords, with the highest being "`r overlap.cart[1,1]`" at `r overlap.cart[1,3]`% followed by "`r overlap.cart[2,1]`" at `r sum(overlap.cart$perc.cart[overlap.cart$keyword=="BHO"])`% of the cartridges. We will have to consider whether to categorize as "cartridge" first, or as oil or BHO, or as something like "BHO cartridge" as compared to "General cartridge", for example. Similarly we need to make the same judgements with other subcategories of cartridges, though there are fewer products in the market with these other combinations of keywords.

```{r, prelimcat_cartridges2, warning=FALSE}
knitr::kable(overlap.cart, col.names = c("Keyword", "% of Inhalants", "% of cartridges", "Count"),
               align=c("r", "r", "r", "r"))

```

### Overlap: Oil

```{r prelimcat_oil, warning=FALSE}

overlap.oil <- inhalants %>%
  # keep only oils
  dplyr::filter(oil) %>%
  # get count of number of oils in df
  dplyr::mutate(oil_count = n()) %>%
  # select only that count of rows in this filtered dataframe,
  # row identifier, and classifications other than oil
  dplyr::select(oil_count, dispensingid, cartridge, BHO:wax) %>%
  # gather to get row identified + column of keywords + column of T/F values
  tidyr::gather(keyword, status, cartridge, BHO:wax) %>%
  # group by keyword to get statistics for each keyword
  dplyr::group_by(keyword) %>%
  dplyr::summarise(
    # percent of all inhalants that are this keyword
    perc.inhalants = round(sum(status==TRUE) / nrow(inhalants)*100,2),
    # percent of oil category that are also this keyword
    # using oil_count[1] because there are many oil_count's, even though they all have
    # the same value, need to tell it to just take the first one
    perc.oil = round(sum(status==TRUE) / oil_count[1] * 100,2),
    # count of this category within oils
    count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc.oil))

```

It also looks like things that are categorized as "oil" are picking up other keywords too. This table looks only at products that have "oil" in the name, and then what other, additional keywords they also pick up, along with the percentage of inhalant market and percentage of "oil" products that also contain that keyword.

It appears that `r sum(overlap.oil$perc.oil[overlap.oil$keyword=="cartridge"])`% of the oils are also listed as cartridges, which is not surprising. It might be best to categorize as "cartridge" first, and "oil" if not a cartridge. Also `r sum(overlap.oil$perc.oil[!overlap.oil$keyword=="cartridge"])`% of "oils" are also picking up other keywords, which is something we could explore further to determine how to categorize. For example, `r overlap.oil[2,3]`% of products that contain the string "oil" also contain the string "`r overlap.oil[2,1]`", and `r overlap.oil[3,3]`% of oil product names also contain the string "`r overlap.oil[3,1]`".

```{r prelimcat_oil2, warning=FALSE}
knitr::kable(overlap.oil, col.names = c("Keyword", "% of Inhalants", "% of Oils", "Count"),
               align=c("r", "r", "r", "r"))
```


