---
title: "Extracts - Processors’ Types"
author: "Lauren Renaud"
date: "May 8, 2017"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(dplyr)
library(readr)
library(knitr)
library(tidyr)
options(scipen = 4)
```

```{r setup2, include=FALSE, cache=TRUE}

# pull in & clean dfs ------
# locatons
locations <- read.csv("../data/Dec2016/cleaned/locations/all_locations.csv", sep=",", header=T)
locations <- select(locations, location_id, name, city, loc_type = typesimp)

# inventory
inventory <- readr::read_csv("../data/Dec2016/biotrackthc_inventory.csv")
inventory$inv_date <- as.Date(as.POSIXct(inventory$sessiontime, 
                                            origin = "1970-01-01", tz="America/Los_Angeles"))
inventory$sample_id <- as.numeric(inventory$sample_id)
inventory$parentid <- as.numeric(inventory$parentid)
# join to inventory types
inventory.types <- read.csv("../data/Dec2016/cleaned/inventory_type.csv", sep=",", header=T)
inventory <- inventory %>%
  # get inventory types
  left_join(inventory.types, by="inventorytype") %>%
  # get location types
  left_join(locations, by=c("location" = "location_id")) %>%
  # drop other location variables
  select(-(name), -(city))
rm(inventory.types)

# selected variables
inv.select <- select(inventory, inventoryid = id, inv_strain = strain, parentid,
                     inv_type_name, inventoryparentid, productname, sample_id,
                     inv_location = location, inv_loctype = loc_type)

# dispensing
dispensing <- readr::read_csv("../data/Dec2016/biotrackthc_dispensing.csv")
dispensing <- filter(dispensing, inventorytype==24)
dispensing$saletime <- as.Date(as.POSIXct(dispensing$sessiontime, 
                                           origin = "1970-01-01", tz="America/Los_Angeles"))
dispens.select <- select(dispensing, dispensingid = id, retail_invid = inventoryid, retail_loc = location,
                         sale_price = price, saletime)
dispens.select <- dispens.select %>%
  left_join(locations, by=c("retail_loc" = "location_id")) %>%
  # drop other location variables
  select(-(name), -(city))


## testing going back one more step then looking at product types
inhalants.joined <- dispens.select %>%
  # first get to retailer's inventory to get `parentid`
  # as well as retail productname, retail strain
  dplyr::left_join(inv.select, by=c("retail_invid" = "inventoryid")) %>%
  # rename to inventory variables to clarify they are retail variables
  rename(retail_strain = inv_strain, retail_parentid = parentid, retail_invtype = inv_type_name,
         retail_invparentid = inventoryparentid, retail_prodname = productname, retail_sampId = sample_id,
         retail_location = inv_location) %>%
  # then use retailer's parentid to get to processor's inventoryid
  left_join(inv.select, by=c("retail_parentid" = "inventoryid")) %>%
  # then rename processor inventory variables
  rename(process_strain = inv_strain, process_parentid = parentid,
         process_invparentid = inventoryparentid, process_invtype = inv_type_name,
         process_prodname = productname, process_sampleid = sample_id, process_loc = inv_location) %>%
  # then use processors's parentid to get to one step further back inventoryid
  # these variables will now be called "inv_variablename"
  left_join(inv.select, by=c("process_invparentid" = "inventoryid"))


# 5% of product names for inhalants are missing, which is ~ the same as in full inventory df
# sum(is.na(inventory$productname[inventory$inventorytype==24])) / sum(inventory$inventorytype==24)
# # 33% are missing for processors' product name
# sum(is.na(inhalants.joined$inv_prodname)) / nrow(inhalants.joined)
# # inventory type
# # missing for 70 of joined inhalants (out of 6 million)
# sum(is.na(inhalants.joined$retail_invtype)) / nrow(inhalants.joined)
# 
# dispeningtypes <- unique(dispensing$inventorytype[!is.na(dispensing$inventorytype)])


# first get list/df of inhalantnames
inhalantnames <- as.data.frame(unique(inhalants.joined$retail_prodname))
# rename column so we can call it
colnames(inhalantnames) <- "retail_prodname"

# get a df that is for each unique inhalant name, the boolean values for categorizing
inhalantnames <- inhalantnames %>%
  dplyr::rowwise() %>%
                 # boolean for cartridge
  dplyr::mutate(cartridge = grepl("cart|vap|vc|pen|refill", retail_prodname, ignore.case = T),
                # categorical
                type = ifelse(
                  grepl("BHO|butane", retail_prodname, ignore.case = T), "BHO",
                  ifelse(grepl("CO2", retail_prodname, ignore.case = T), "CO2",
                         ifelse(grepl("hash", retail_prodname, ignore.case = T), "hash",
                                ifelse(grepl("hash", retail_prodname, ignore.case = T), "kief",
                                       ifelse(grepl("bubble", retail_prodname, ignore.case = T), "bubble",
                                              ifelse(grepl("shatter", retail_prodname, ignore.case = T), "shatter",
                                                     ifelse(grepl("dab", retail_prodname, ignore.case = T), "dab",
                                                            ifelse(grepl("resin", retail_prodname, ignore.case = T), "resin",
                                                                   ifelse(grepl("wax", retail_prodname, ignore.case = T), "wax",
                                                                          "other"))))))))
                ),
                # now booleans for each
                oil = grepl("oil", retail_prodname, ignore.case = T),
                CO2 = grepl("CO2", retail_prodname, ignore.case=T),
                BHO = grepl("BHO|butane", retail_prodname, ignore.case = T),
                hash = grepl("hash", retail_prodname, ignore.case = T),
                kief = grepl("kief|keif", retail_prodname, ignore.case = T),
                bubble = grepl("bubble", retail_prodname, ignore.case = T),
                shatter = grepl("shatter", retail_prodname, ignore.case = T),
                dab = grepl("dab", retail_prodname, ignore.case = T),
                resin = grepl("resin", retail_prodname, ignore.case = T),
                wax = grepl("wax", retail_prodname, ignore.case = T),
                uncategorized = (!cartridge & !CO2 & !oil & !BHO & !kief & !bubble & !shatter & !dab & !resin & !wax),
                uncat_notcart = (!CO2 & !oil & !BHO & !kief & !bubble & !shatter & !dab & !resin & !wax)
  )

# join classified inhalantnames back to dispening df
inhalants.joined$retail_prodname <- as.factor(inhalants.joined$retail_prodname)
inhalants <- left_join(inhalants.joined, inhalantnames, by="retail_prodname")

prelimCat <- inhalants %>%
  dplyr::select(dispensingid, cartridge:uncategorized) %>%
  tidyr::gather(keyword, status, cartridge:uncategorized) %>%
  dplyr::group_by(keyword) %>%
  dplyr::summarise(perc = round(sum(status==TRUE) / nrow(inhalants)*100,1),
                   count = sum(status==TRUE)) %>%
  dplyr::arrange(desc(perc))

# trying to get count of how many products hit more than category
# doing just based on names, not actual number of products
# because full df was long to run, but could check again later
num.keywords <- inhalantnames %>%
  tidyr::gather(keyword, status, cartridge:uncategorized) %>%
  dplyr::group_by(retail_prodname) %>%
  dplyr::summarise(numCat = sum(status==TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(numCat) %>%
  dplyr::summarise(distro_numkeywords = n(),
                   perc_numkeywords = n() / nrow(inhalantnames))
```

# Processor Types

We can look at the processors' inventory types to as a way to classify those that were "uncategorized", as well as to double check our above classifications.

For about half of the inhalants, the processor also listed the product type as "Marijuana Extract for Inhalation", but for the other half, we have more detail about what went into the product. It also may be possible, if needed or useful, to try to go back one further step in the suppy chain to see what inventory types came before "Marijuana Extract for Inhalation" for a given product.

```{r processortypes, warning=FALSE}
# combinations of inventory types
process.types <- inhalants %>%
  # for some reason there is a very small number that are missing retail inventory type
  # that didn't wokr in the join correctly
  # screening these 70 out, but might investigate why
  filter(!is.na(retail_invtype)) %>%
  # group by processor's inventory type to get count and stats of the combinations
  group_by(process_invtype) %>%
  summarise(perc = round( n() / nrow(inhalants.joined)*100,1),
            count = n()) %>%
  arrange(desc(count))

knitr::kable(process.types, col.names = c("Processor's Inventory Type - All Inhalants",
                                          "Percent of Inhalants",
                                          "Count"),
               align=c("r", "r", "r"))


process.types.uncategorized <- inhalants %>%
  # same as above, but restricted to inhalants that are uncategorized
  filter(!is.na(retail_invtype), uncategorized) %>%
  # get count of number of uncategorized
  mutate(total = n()) %>%
  group_by(process_invtype) %>%
  summarise(perc = round(n() / total[1] *100,1),
            count = n()) %>%
  arrange(desc(count))

```

More excitingly, we should be able to classify an additional `r round(sum(process.types.uncategorized$perc[process.types.uncategorized$process_invtype!="Marijuana Extract for Inhalation" & process.types.uncategorized$process_invtype!="Food Grade Solvent Extract" & !is.na(process.types.uncategorized$process_invtype)]),1)`% of the inhalants that we were not able to categorized by product name and keywords by looking at the processor's listed inventory types. This should allow us to get our uncategorized products down to about `r round(sum(inhalants$uncategorized, na.rm=T) / nrow(inhalants) * (sum(process.types.uncategorized$perc[process.types.uncategorized$process_invtype!="Marijuana Extract for Inhalation" & process.types.uncategorized$process_invtype!="Food Grade Solvent Extract"], na.rm=T)/100)*100,1)`% of inhalants.

```{r processortypes2, warning=FALSE}

knitr::kable(process.types.uncategorized, col.names = c("Processor's Inventory Type - Only Uncategorized",
                                                        "Percent of Uncategorized",
                                                        "Count"),
             align=c("r", "r", "r"))

```

# Next Steps

 - Explore the still uncategorized extracts to see if they have any time, price, potency, etc trends
 - Explore the `r round(sum(num.keywords$distro_numkeywords[num.keywords$numCat>1]) / nrow(inhalantnames)*100,1)`% of overlapping keyword classifications and determine how to categorize them
 - Scatterplot of existing categories, possible cluster model, which may also help classify the uncategorized
 - Possibly aggregage back up into more generalized inhalant categories like "cartridge", "concentrate", "other", or something else that more generally captures either use-type, potency cluster, or both
 - Use these categories for futher analysis of the extract market

