---
title: "Lab gif"
author: "Krista Kinnard"
date: "February 26, 2017"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
library(readr)
library(lubridate)
library(stringr)
library(plotly)
library(gridExtra)
```

*General intro text about why we're looking at fail rates?*

```{r, echo=FALSE, warning=FALSE}

# read in the data
fmt <- read.csv("../data/Dec2016/cleaned/samples/fail_merge_time.csv")
lab_codes <- read.csv("../data/Dec2016/cleaned/locations/lab_codes.csv")

# fix the dates -----------------------------------------------
# Convert to mdy
fmt$date <- mdy(fmt$test_date)
# Get month and year
fmt$month <- month(as.POSIXlt(fmt$date, format="%d/%m/%Y"))
# Get year
fmt$year <- year(as.POSIXlt(fmt$date, format="%d/%m/%Y"))
# Get month year
fmt$month_Yr <- format(as.Date(fmt$date), "%Y-%m")


# Fail Rate for Micro Tests
micro_all <- fmt %>%
  dplyr::select(lab_id, Test, num_fail, total_tests, month_Yr) %>%
  dplyr::filter(Test == "Micro Screen") %>% # Subset to Micro Screen only
  dplyr::arrange(month_Yr) %>%
  dplyr::group_by(lab_id, month_Yr) %>%
  dplyr::summarise(month_fail = sum(num_fail), month_tot = sum(total_tests)) %>%
  dplyr::mutate(mo_fail_rate = month_fail/month_tot) %>%
  dplyr::group_by(lab_id) %>%
  dplyr::mutate(lab_tot = cumsum(month_tot)) %>%
  dplyr::filter(month_tot > 200) 

# 
# 
# t <- list(
#   family = "arial black",
#   size = 18,
#   color = toRGB("black"))
# 
# x <- list(
#   title = 'Cumulative Number of Tests Processed'
# )
# y <- list(
#   title = 'Monthly Fail Rate'
# )
# 
# base <- micro_all %>%
#   plot_ly(x = ~lab_tot, y = ~mo_fail_rate,  mode = "markers",
#           text = ~lab_id, hoverinfo = "text",
#   marker = list(size = 40,
#               color = 'limegreen',
#               line = list(color = 'darkgreen',
#                           width = 2))) %>%
#   layout(title = 'Lab Fail Rate over Time',
#          yaxis = y,
#          xaxis = x)
# 
# base %>%
#   add_markers(frame = ~month_Yr, ids = ~lab_id) %>%
#   animation_opts(1000, easing = "elastic", transition = 0) %>%
#   animation_button(
#     x = 1, xanchor = "right", y = 0, yanchor = "bottom"
#   ) %>%
#   animation_slider(
#     currentvalue = list(prefix = "Month & Year ", font = list(color="red"))
#   ) %>%
#   add_text(textfont = t, textposition = "center") %>%
#   hide_legend()

```


### Lab Fail Rates Over Time

It appears that often when a new lab initially opens, there may be high fail rates that then come down over time. While this may in part be due to the newness of the legal market overall, when we look at the fail rate given the number of months a lab has been open as opposed to their fail rate over time that the market has been open, this spike appears to be more closely related to the lab opening than to the market opening.

```{r, failovertimebylab, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4, fig.align='center'}

#fail_merge <- read.csv("../data/Dec2016/cleaned/samples/fail_merge.csv")
fail_merge_time <- read.csv("../data/Dec2016/cleaned/samples/fail_merge_time.csv")
# convert to dates
fail_merge_time$test_date <- as.Date(fail_merge_time$test_date, format="%m/%d/%Y")
# get month of the test for grouping
fail_merge_time$month <- floor_date(fail_merge_time$test_date, "month")
# connect codes
fail_merge_time <- left_join(fail_merge_time, lab_codes, by="lab_id")

bymonth <- fail_merge_time %>%
  group_by(code, month) %>%
  summarise(failrate = sum(num_fail, na.rm=T) / sum(total_tests, na.rm=T)) %>%
  ggplot(aes(x=month, y=failrate, group=code)) +
  geom_line(color="darkseagreen") +
  scale_y_continuous(labels = scales::percent) +
  labs(title="Fail Rate Over Time",
       x="Month",
       y="Fail Rate") + 
  theme(panel.background = element_rect(fill = "white"))

# same graph, but for months lab has been open
byopen <- fail_merge_time %>%
  group_by(code) %>%
  mutate(months_open = as.numeric((month - min(month)) / 30)) %>%
  group_by(code, months_open) %>%
  summarise(failrate = sum(num_fail, na.rm=T) / sum(total_tests, na.rm=T)) %>%
  rename(`Lab` = code, `Months Open` = months_open, `Fail Rate` = failrate) %>%
  ggplot(aes(x=`Months Open`, y=`Fail Rate`, group=`Lab`)) +
  geom_line(color="darkseagreen") +
  scale_y_continuous(labels = scales::percent) +
  labs(title="Fail Rate by Months Open",
       x="Months Open",
       y="Fail Rate") + 
  theme(panel.background = element_rect(fill = "white"))
        #, panel.grid.major = element_line(colour = "lightgrey"))

#names(fail_merge_time)

grid.arrange(bymonth, byopen, ncol=2)
```

#### Lab Fail Rates by Months Open

```{r monthsopen, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=4.5, fig.align='center'}

ggplotly(byopen)

# fail_merge_time %>%
#   group_by(code) %>%
#   mutate(months_open = (month - min(month)) / 30) %>%
#   group_by(code, months_open) %>%
#   summarise(failrate = sum(num_fail, na.rm=T) / sum(total_tests, na.rm=T)) %>%
#   plot_ly(
#   x = ~months_open, y = ~failrate,
#   mode = 'lines',
#   colors = "darkseagreen",
#   text = ~paste("Lab: ", code, "<br /> Months Open: ", round(months_open, 0), "<br /> Fail Rate: ", round(failrate, 2)))
#   
# fail_merge_time %>%
#   group_by(code) %>%
#   mutate(months_open = (month - min(month)) / 30) %>%
#   group_by(code, months_open) %>%
#   summarise(failrate = sum(num_fail, na.rm=T) / sum(total_tests, na.rm=T)) %>%
#   plot_ly(
#   x = ~months_open, y = ~failrate,
#   #mode = 'lines',
#   text = ~paste("Lab: ", code, "<br /> Months Open: ", round(months_open, 0), "<br /> Fail Rate: ", round(failrate, 2))
#   ) %>%
#   #text = ~paste("Price: ", price, '$<br>Cut:', cut)) %>%
#   add_lines(colors = "black", alpha = 0.6)

```

### Lab Fail Rates and Number of Tests Over Time
Text here about what it means. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Fail Rate for Micro Tests
all <- fmt %>%
  dplyr::select(lab_id, Test, num_fail, total_tests, month_Yr) %>%
  dplyr::arrange(month_Yr) %>%
  dplyr::group_by(lab_id, month_Yr) %>%
  dplyr::summarise(month_fail = sum(num_fail), month_tot = sum(total_tests)) %>% # Calculate the monthly fails
  dplyr::mutate(mo_fail_rate = month_fail/month_tot) %>% # Calculate the monthly fail rate
  dplyr::group_by(lab_id) %>%
  dplyr::mutate(lab_tot = cumsum(month_tot)) %>% # Calculate the cumulative sum of samples received
  dplyr::filter(month_tot > 200) %>% # limit to months that received > 200 samples
  dplyr::left_join(lab_codes, by = "lab_id") # bring in lab codes to deidentify

# Set fonts to text
t <- list(
  family = "arial black",
  size = 18,
  color = toRGB("black"))
# Set X-axis
x <- list(
  title = 'Cumulative Number of Tests Processed'
)
# Set y-axis
y <- list(
  title = 'Monthly Fail Rate'
)

# Set up plot
base <- all %>%
  plot_ly(x = ~lab_tot, y = ~mo_fail_rate,  mode = "markers", # x=cumulative total y=monthly fail rate
          text = ~code, hoverinfo = "text", # put text as lable on circles
  marker = list(size = 40, # set color and size of circles
              color = 'limegreen',
              line = list(color = 'darkgreen',
                          width = 2))) %>%
  layout(title = 'Lab Fail Rate over Time',
         yaxis = y,
         xaxis = x) 

base %>%
  add_markers(frame = ~month_Yr, ids = ~code) %>% # include animation over time
  animation_opts(1000, easing = "elastic", transition = 0) %>% # control speed of animation
  animation_button(
    x = 1, xanchor = "right", y = 0, yanchor = "bottom" # place the play button
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "Month & Year ", font = list(color="red")) # ad count to slider (not working) 
  ) %>%
  add_text(textfont = t, textposition = "center") %>%
  hide_legend()

```
