---
title: "Sys Project"
author: "Yilun Bao"
date: 'January 19 2017'
output: 
  html_document:
    toc: true
    toc_depth: 3
---

#### **Data Preview & Preprocessing**

```{r}
# Import Retail Analysis dataset.
# retail.pre <- read.csv("border_stores.csv", header=TRUE)
# idaho <- read.csv("idaho_border.csv", header = TRUE)
# oregon <- read.csv("oregon_border.csv", header = TRUE)

# Import packages.
library(plyr)
library(knitr)
library(ggplot2)
library(gridExtra)

# Set the scientific notation.
# options(scipen = 7)
```
  
Split the dataset.

```{r}
# recreate the csv file.
# idaho <- idaho[1:7, 1:11]
# oregon <- oregon[1:13, 1:11]

# get individual csv for each store.
# 2 stores in Clarkston
# i.810 <- retail.pre[which(retail.pre$location == 810),]
# i.887 <- retail.pre[which(retail.pre$location == 887),]

# 4 stores close to State University WA
# pm.457 <- retail.pre[which(retail.pre$location == 457),]
# pm.910 <- retail.pre[which(retail.pre$location == 910),]
# pm.1751 <- retail.pre[which(retail.pre$location == 1751),]
# pm.1761 <- retail.pre[which(retail.pre$location == 1761),]

# 1 store in Pullman a bit far away from the campus
# pm.1874 <- retail.pre[which(retail.pre$location == 1874),]
```

Clarkston

```{r}
# 810 exploration
# CANNA4LIFE, Retailer & Medical
i.810 <- read.csv("idaho_810.csv", header = TRUE)
# Deal with the Date
i.810$date <- substr(as.character(i.810$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.810 <- ddply(i.810, .(date), summarize, trans = length(name))
sum.tran.810$date <- as.Date(sum.tran.810$date, format="%Y-%m-%d")

# Plot the number of transactions
ggplot(data = sum.tran.810, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "810 Number of Transactions \n (2015-05-22 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```

```{r}
# 887 exploration
# GREENFIELD COMPANY CANNABIS MERCANTILE, Retailer & Medical
i.887 <- read.csv("idaho_887.csv", header = TRUE)
# Deal with the Date
i.887$date <- substr(as.character(i.887$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.887 <- ddply(i.887, .(date), summarize, trans = length(name))
sum.tran.887$date <- as.Date(sum.tran.887$date, format="%Y-%m-%d")

ggplot(data = sum.tran.887, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "887 Number of Transactions \n (2014-12-03 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```

Pullman

```{r}
# 457 exploration
# MJ'S POT SHOP, Retailer & Medical
pm.457 <- read.csv("pullman_457.csv", header = TRUE)
# Deal with the Date
pm.457$date <- substr(as.character(pm.457$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.457 <- ddply(pm.457, .(date), summarize, trans = length(name))
sum.tran.457$date <- as.Date(sum.tran.457$date, format="%Y-%m-%d")


ggplot(data = sum.tran.457, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "457 Number of Transactions \n (2014-11-04 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
# 1761 exploration
# MJ'S POT SHOP, Retailer
pm.1761 <- read.csv("pullman_1761.csv", header = TRUE)
# Deal with the Date
pm.1761$date <- substr(as.character(pm.1761$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.1761 <- ddply(pm.1761, .(date), summarize, trans = length(name))
sum.tran.1761$date <- as.Date(sum.tran.1761$date, format="%Y-%m-%d")


ggplot(data = sum.tran.1761, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "1761 Number of Transactions \n (2014-09-26 to 2015-04-24)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```

```{r}
# Composite file for MJ's Shop
sum_MJ <- rbind(sum.tran.457, sum.tran.1761)
sum_MJ <- ddply(sum_MJ, .(date), summarize, trans = sum(trans))

ggplot(data = sum_MJ, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "MJ'S POT SHOP Number of Transactions \n (2014-09-26 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```


```{r}
# 910 exploration
# WE'RE JUST BUDS, Retailer & Medical
pm.910 <- read.csv("pullman_910.csv", header = TRUE)
# Deal with the Date
pm.910$date <- substr(as.character(pm.910$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.910 <- ddply(pm.910, .(date), summarize, trans = length(name))
sum.tran.910$date <- as.Date(sum.tran.910$date, format="%Y-%m-%d")


ggplot(data = sum.tran.910, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "910 Number of Transactions \n (2015-03-09 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
# 1751 exploration
# SATORI, Retailer & Medical
pm.1751 <- read.csv("pullman_1751.csv", header = TRUE)
# Deal with the Date
pm.1751$date <- substr(as.character(pm.1751$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.1751 <- ddply(pm.1751, .(date), summarize, trans = length(name))
sum.tran.1751$date <- as.Date(sum.tran.1751$date, format="%Y-%m-%d")


ggplot(data = sum.tran.1751, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "1751 Number of Transactions \n (2015-11-23 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```


```{r}
# Composite file for Pullman 4 stores
sum_pm <- rbind(sum_MJ, sum.tran.910, sum.tran.1751)
sum_pm <- ddply(sum_pm, .(date), summarize, trans = sum(trans))

ggplot(data = sum_pm, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Pullman 4 Stores Number of Transactions \n (2014-09-26 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```




```{r}
# 1874 exploration
# PABLO & CO., LLC, Retailer & Medical
pm.1874 <- read.csv("pullman_1874.csv", header = TRUE)
# Deal with the Date
pm.1874$date <- substr(as.character(pm.1874$monthtime), 1, 10)
# Calculate the number of transactions
sum.tran.1874 <- ddply(pm.1874, .(date), summarize, trans = length(name))
sum.tran.1874$date <- as.Date(sum.tran.1874$date, format="%Y-%m-%d")


ggplot(data = sum.tran.1874, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "1874 Number of Transactions \n (2015-09-21 to 2016-10-29)") + theme(text = element_text(size = 7), axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))
```


```{r}
# Composite file for Pullman 5 stores
sum_pm_all <- rbind(sum_pm, sum.tran.1874)
sum_pm_all <- ddply(sum_pm_all, .(date), summarize, trans = sum(trans))

ggplot(data = sum_pm_all, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Pullman 5 Stores Number of Transactions \n (2014-09-26 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```


```{r}
# Other 3 College Towns
# Import the required files
retailer <- read.csv("stores_by_totalsales.csv", header = TRUE)
date.file <- read.csv("retail_times.csv", header = TRUE)

# Merge the date columns onto retailer
colnames(date.file)[1] <- "location"
co.retailer <- merge(retailer, date.file, by = 'location', all.x = TRUE)
co.retailer <- co.retailer[,c(1:11, 22:24)]

# Import the transaction data.
trans <- read.csv("sales_bystore_byday.csv")
colnames(trans)[4] <- "trans"
```



```{r}
library(dplyr)
countstores_byday <- ddply(trans, "date", summarize, num_stores = length(location))
Average_Daily_Sales<-trans %>%
  group_by(date)%>%
  dplyr::summarise(Daily.transactions = sum(trans),Daily.Revenue = sum(total_sales))%>%
  merge(countstores_byday,by = 'date')%>%
  mutate(avg.daily.transactions=Daily.transactions/num_stores,avg.daily.revenue=Daily.Revenue/num_stores)


```


Kittitas County
Central Uni

```{r}
# Select the retailer info from the Retailer
kitt <- co.retailer[which(co.retailer$location == 308|co.retailer$location == 981|co.retailer$location == 1637|co.retailer$location == 1813), ]
```

```{r}
# 981
# The Green Shelf, Retailer & Medical
k.981 <- trans[which(trans$location == 981),]
# Form the Date column
k.981$date <- as.Date(k.981$date, format="%Y-%m-%d")

ggplot(data = k.981, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores 981 Number of Transactions \n (2015-02-02 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

ggplot(k.981, mapping = aes(x = date, y = trans)) + geom_point(size = 2.5, color = "#56B4E9") + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs(x ="Date", y = "Number of Transactions", title = "Kittitas Stores 981 Number of Transactions \n (2015-02-02 to 2016-10-31)") + geom_line(data=Average_Daily_Sales[50:848,], mapping=(aes(x=as.Date(date),y=avg.daily.transactions)), group=1)
```

```{r}
# 1813
# The Fire House, Retailer & Medical
k.1813 <- trans[which(trans$location == 1813),]
# Form the Date column
k.1813$date <- as.Date(k.1813$date, format="%Y-%m-%d")

ggplot(data = k.1813, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores 1813 Number of Transactions \n (2016-03-16 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
# 308
# Cannabis Central, Retailer
k.308 <- trans[which(trans$location == 308),]
# Form the Date column
k.308$date <- as.Date(k.308$date, format="%Y-%m-%d")

ggplot(data = k.308, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores 308 Number of Transactions \n (2014-08-18 to 2016-04-07)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
# 1637
# Cannabis Central, Retailer & Medical
k.1637 <- trans[which(trans$location == 1637),]
# Form the Date column
k.1637$date <- as.Date(k.1637$date, format="%Y-%m-%d")

ggplot(data = k.1637, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores 1637 Number of Transactions \n (2015-06-04 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
# Composite file for one store
# Cannabis Central, Retailer & Medical
cnb_ct <- rbind(k.308, k.1637)
cnb_ct <- ddply(cnb_ct, .(date), summarize, trans = sum(trans))
cnb_ct$date <- as.Date(cnb_ct$date, format="%Y-%m-%d")

ggplot(data = cnb_ct, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores Cannabis Central Number of Transactions \n (2014-08-18 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

ggplot(cnb_ct, mapping = aes(x = date, y = trans)) + geom_point(size = 2.5, color = "#56B4E9") + ylim(0, 1000) + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores Cannabis Central Number of Transactions \n (2014-08-18 to 2016-10-31)") + geom_line(data=Average_Daily_Sales[50:848,], mapping=(aes(x=as.Date(date),y=avg.daily.transactions)), group=1)
```

```{r}
# Composite file for Kittitas
sum_kitt <- rbind(k.981, k.1813, k.308, k.1637)
sum_kitt <- ddply(sum_kitt, .(date), summarize, trans = sum(trans))
sum_kitt$date <- as.Date(sum_kitt$date, format="%Y-%m-%d")

ggplot(data = sum_kitt, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores: Number of Transactions \n (2014-08-18 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

ggplot(sum_kitt, mapping = aes(x = date, y = trans)) + geom_point(size = 2.5, color = "#56B4E9") + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs( x ="Date", y = "Number of Transactions", title = "Kittitas Stores: Number of Transactions \n (2014-08-18 to 2016-10-31)") + geom_line(data=Average_Daily_Sales[50:848,], mapping=(aes(x=as.Date(date),y=avg.daily.transactions)), group=1)
```



ggplot(sum_kitt, mapping = aes(x = date, y = trans)) + geom_point(color = "#56B4E9") + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs(title="Kittitas Stores: Number of Transactions \n (2014-08-18 to 2016-10-31)") +
  geom_vline(xintercept= as.numeric(as.Date('2015-1-12')),linetype="dashed", size=1, colour="grey") +
  geom_vline(xintercept= as.numeric(as.Date('2015-3-16')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-3-20')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-8')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-11')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-1')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-24')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-12-18')),linetype="dashed", size=1, colour="grey")+
  geom_line(data=AvgDailySale2015,
            mapping=(aes(x=as.Date(date),y=avg.daily.transactions)),
            group=1)





Walla Walla 
Walla Walla Community
WW University
Whitman College

```{r}
# Select the retailer info from the Retailer
walla <- co.retailer[which(co.retailer$location == 1101|co.retailer$location == 1144), ]
```

```{r}
# 1101
# Walla Walla Weedery, Retailer & Medical
w.1101 <- trans[which(trans$location == 1101),]
# Form the Date column
w.1101$date <- as.Date(w.1101$date, format="%Y-%m-%d")

ggplot(data = w.1101, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Walla Walla Stores 1101 Number of Transactions \n (2015-04-16 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

ggplot(w.1101, mapping = aes(x = date, y = trans)) + geom_point(size = 2.5, color = "#56B4E9") + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs(x ="Date", y = "Number of Transactions", title = "Walla Walla Stores 1101 Number of Transactions \n (2015-04-16 to 2016-10-31)") + geom_line(data=Average_Daily_Sales[429:848,], mapping=(aes(x=as.Date(date),y=avg.daily.transactions)), group=1)
```

```{r}
# 1144
# Walla Walla Cannabis Company, Retailer & Medical
w.1144 <- trans[which(trans$location == 1144),]
# Form the Date column
w.1144$date <- as.Date(w.1144$date, format="%Y-%m-%d")

ggplot(data = w.1144, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Walla Walla Stores 1144 Number of Transactions \n (2014-12-14 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

ggplot(w.1144, mapping = aes(x = date, y = trans)) + geom_point(size = 2.5, color = "#56B4E9") + ylim(0, 2000) + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs(x ="Date", y = "Number of Transactions", title = "Walla Walla Stores 1144 Number of Transactions \n (2014-12-14 to 2016-10-31)") + geom_line(data=Average_Daily_Sales[429:848,], mapping=(aes(x=as.Date(date),y=avg.daily.transactions)), group=1)
```

```{r}
# Composite file for Walla Walla
sum_walla <- rbind(w.1101, w.1144)
sum_walla <- ddply(sum_walla, .(date), summarize, trans = sum(trans))
sum_walla$date <- as.Date(sum_walla$date, format="%Y-%m-%d")

ggplot(data = sum_walla, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Walla Walla Stores Number of Transactions \n (2014-12-14 to 2016-10-31)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
ggplot(sum_walla, mapping = aes(x = date, y = trans)) + geom_point(size = 2.5, color = "#56B4E9") + geom_smooth(method='lm', formula = y~ns(x, df=10),color ="#009E73" ) + labs(title="Walla Walla Stores: Number of Transactions \n (2014-12-14 to 2016-10-31)") + geom_line(data=Average_Daily_Sales[429:848,], mapping=(aes(x=as.Date(date),y=avg.daily.transactions)), group=1)
```


Benson
Columbia Basin College
956

```{r}
# Select the retailer info from the Retailer
benson <- co.retailer[which(co.retailer$location == 956), ]
```

```{r}
# 956
# Lucky Leaf, Retailer
b.956 <- trans[which(trans$location == 956),]
# Form the Date column
b.956$date <- as.Date(b.956$date, format="%Y-%m-%d")

ggplot(data = b.956, mapping = aes(x = date, y = trans)) + geom_point() + labs( x ="Date", y = "Number of Transactions", title = "Benson Store 956 Number of Transactions \n (2015-03-11 to 2015-08-14)") + theme(text = element_text(size = 9), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```






