---
title: "System_Yutian"
author: "Yutian Guo"
date: "February 28, 2017"
output: html_document
---

############ Library #################
```{r setup, include=FALSE}
library(ggplot2)
library(MASS)
library(caret)
library(knitr)
library(dplyr)
library(plyr)
library(data.table) 
library(reshape2)
library(lubridate) #date-time stuff
library(splines)
library(hexbin) #geom_hexbin
library(broom)

```

############ Load Data ###############

```{r,cache=TRUE}
countstores_byday <- read.csv("countstores_byday.csv",header = TRUE)
sales_bystore_byday <- read.csv("sales_bystore_byday.csv",header = TRUE)
border_stores.csv <- read.csv("border_stores.csv",header = TRUE)
pullman_all_stores<- border_stores.csv[which(border_stores.csv$location %in% getPullmanStores),]
write.csv(file = 'pullman_all_stores', pullman_all_stores)

```



############ Modify Data ############### 

Color Schema

```{r }



# The palette with black:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# To use for fills, add
  scale_fill_manual(values=cbPalette)

# To use for line and point colors, add
  scale_colour_manual(values=cbPalette)

```


### Add Attributes ###

```{r pressure, echo=FALSE}
# Add column Year Month to it
sales_bystore_byday$date <- as.Date(sales_bystore_byday$date)
countstores_byday$date <- as.Date(countstores_byday$date)
# Year
countstores_byday$year<- as.numeric(format(countstores_byday$date,'%Y'))
sales_bystore_byday$year <-as.numeric(format(sales_bystore_byday$date,'%Y'))
# Month
countstores_byday$month<- as.numeric(format(countstores_byday$date,'%m'))
sales_bystore_byday$month <-as.numeric(format(sales_bystore_byday$date,'%m'))
# Day
countstores_byday$mday<- as.numeric(format(countstores_byday$date,'%d'))
sales_bystore_byday$mday <-as.numeric(format(sales_bystore_byday$date,'%d'))

# Weekdays

countstores_byday$wday <- weekdays(countstores_byday$date)
sales_bystore_byday$wday <- weekdays(sales_bystore_byday$date)

# Make Location factor
sales_bystore_byday$location <- as.factor(sales_bystore_byday$location)


# Add adjust store open time 
sales_bystore_byday<-sales_bystore_byday%>%
  group_by(location)%>%
  mutate(open_time = date-min(date))



```




### add holiday 2014 - 2016
If holiday
```{r }

holiday <- rep(0, nrow(countstores_byday))
#Martin Luther King Day
holiday[which(countstores_byday$year ==2014 & countstores_byday$month == 1 & countstores_byday$mday == 20)] = 1
holiday[which(countstores_byday$year ==2015 & countstores_byday$month == 1 & countstores_byday$mday == 19)] = 1
holiday[which(countstores_byday$year ==2016 & countstores_byday$month == 1 & countstores_byday$mday == 18)] = 1
#President Day
holiday[which(countstores_byday$year ==2014 & countstores_byday$month == 2 & countstores_byday$mday == 17)] = 1
holiday[which(countstores_byday$year ==2015 & countstores_byday$month == 2 & countstores_byday$mday == 16)] = 1
holiday[which(countstores_byday$year ==2016 & countstores_byday$month == 2 & countstores_byday$mday == 15)] = 1
# 4.20
holiday[which(countstores_byday$month == 4 & (countstores_byday$mday == 20))] = 1
#Memorial Day
holiday[which(countstores_byday$year ==2014 &countstores_byday$month== 5 & countstores_byday$mday == 26)] = 1
holiday[which(countstores_byday$year ==2015 & countstores_byday$month== 5 & countstores_byday$mday == 25)] = 1
holiday[which(countstores_byday$year ==2016 & countstores_byday$month== 5 & countstores_byday$mday == 30)] = 1

#Independence Day
holiday[which(countstores_byday$month == 7 & countstores_byday$mday == 4)] = 1

#Labor Day
holiday[which(countstores_byday$year ==2014 & countstores_byday$month== 9 & countstores_byday$mday == 1)] = 1
holiday[which(countstores_byday$year ==2015 & countstores_byday$month== 9 & countstores_byday$mday == 7)] = 1
holiday[which(countstores_byday$year ==2016 & countstores_byday$month== 9 & countstores_byday$mday == 5)] = 1
#Columbus Day
holiday[which(countstores_byday$year ==2014 & countstores_byday$month== 10 & countstores_byday$mday == 13)] = 1
holiday[which(countstores_byday$year ==2015 & countstores_byday$month== 10 & countstores_byday$mday == 12)] = 1
holiday[which(countstores_byday$year ==2016 & countstores_byday$month== 10 & countstores_byday$mday == 10)] = 1
# Veterance Day
holiday[which(countstores_byday$month == 11 & (countstores_byday$mday == 10 | countstores_byday$mday == 11 | countstores_byday$mday== 12))] = 1
#Thanksgiving
holiday[which(countstores_byday$year ==2014 & countstores_byday$month== 11 & countstores_byday$mday == 27)] = 1
holiday[which(countstores_byday$year ==2015 & countstores_byday$month== 11 & countstores_byday$mday == 26)] = 1
holiday[which(countstores_byday$year ==2016 & countstores_byday$month== 11 & countstores_byday$mday == 24)] = 1
#Christmas
holiday[which(countstores_byday$month == 12 & countstores_byday$mday == 25)] = 1
# Canadian 
holiday[which(countstores_byday$month == 7 & (countstores_byday$mday == 1 ))] = 2

countstores_byday = data.frame(countstores_byday, if.holiday = holiday)

# add holiday to sales_bystore_byday
sales_bystore_byday<-countstores_byday%>%
  select(date,if.holiday)%>%
  merge(sales_bystore_byday,by="date")

```


#### Make Avg Daily Data and Avg 2015 ###

```{r}

# AVG DAILY SALES

Average_Daily_Sales<-sales_bystore_byday %>%
  group_by(date)%>%
  dplyr::summarise(Daily.transactions = sum(total_transactions),Daily.Revenue = sum(total_sales))%>%
  merge(countstores_byday,by = 'date')%>%
  mutate(avg.daily.transactions=Daily.transactions/num_stores,avg.daily.revenue=Daily.Revenue/num_stores)

# AVG 2015
AvgDailySale2015<-subset(Average_Daily_Sales, year == '2015')

```


### Deseason Avg Daily Data ###
```{r}
############ Avg Daily Data Deseasonality ##########

# caculate weekly avg per day = weekTotal / days in week
# caculate daily/weekavg
AvgDailySale2015$week<-week(AvgDailySale2015$date)

AvgDailySale2015_beta<-AvgDailySale2015%>%
  group_by(week)%>%
  dplyr::summarise(daysInWeek = n(),Week.TOTSales = sum(Daily.transactions),
                   Week.TOTRevenue = sum(Daily.Revenue))%>%
  mutate(weekly.avgSales = Week.TOTSales/daysInWeek,
         weekly.avgRevenue =Week.TOTRevenue/daysInWeek)%>%
  merge(AvgDailySale2015,by = "week")%>%
  mutate(DailyTran.dividby.weekAvg= Daily.transactions/weekly.avgSales,
         DailyRev.dividby.weekAvg = Daily.Revenue/weekly.avgRevenue)

# caculate Sales.WeeklyRatio and Revenue.WeeklyRatio = (daily/weekavg)/#weeks in 2015
AvgDailySale2015_seasonality<-AvgDailySale2015_beta%>%
  group_by(wday)%>%
  dplyr::summarise(Sales.WeeklyRatio = sum(DailyTran.dividby.weekAvg)/n(),
                   Revenue.WeeklyRatio = sum(DailyRev.dividby.weekAvg)/n())
# order seasonality 
AvgDailySale2015_seasonality$wday <- factor(AvgDailySale2015_seasonality$wday , levels= c("Sunday", "Monday", 
    "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))

AvgDailySale2015_seasonality<-AvgDailySale2015_seasonality[order(AvgDailySale2015_seasonality$wday), ]

# view seasonality indix
kable(AvgDailySale2015_seasonality)

# merge seasonality to beta version
AvgDailySale2015_beta<-AvgDailySale2015_beta%>%
  merge(AvgDailySale2015_seasonality,by = 'wday')%>%
  arrange(date)

# modify AvgDailySale2015; deseasonal data= daily.Rev / weeklyRatio for that weekday
AvgDailySale2015<-AvgDailySale2015_beta%>%
  select(date,year,month,mday,week,daysInWeek,wday,if.holiday,
         Daily.transactions, Daily.Revenue,Sales.WeeklyRatio,Revenue.WeeklyRatio, num_stores,
         perstore_dailytrans = avg.daily.transactions,perstore_dailyRev = avg.daily.revenue)%>%
  mutate(adj.daily.revenue = Daily.Revenue/Revenue.WeeklyRatio,
         adj.daily.trans =  Daily.transactions/Sales.WeeklyRatio,
         perstore_adj.daily.rev = adj.daily.revenue/num_stores,
         perstore_adj.daily.trans = adj.daily.trans/num_stores)

# SALE 2015
sales_bystore_byday2015<-subset(sales_bystore_byday, year == '2015')



```


### College Town Pullman ###

```{r}
########### PULLMAN ##########
getPullmanStores<- c("457","910","1751","1761","1874")
pullman2015<- sales_bystore_byday2015[which(sales_bystore_byday2015$location %in% getPullmanStores),]

# aggregate on daily
AvgDaily_pullman2015<-pullman2015 %>%
  group_by(date)%>%
  dplyr::summarise(Daily.transactions = sum(total_transactions),Daily.Revenue = sum(total_sales))%>%
  merge(countstores_byday,by = 'date')%>%
  mutate(perstore_dailytrans=Daily.transactions/num_stores,perstore_dailyRev=Daily.Revenue/num_stores)

AvgDaily_pullman2015$week <- week(AvgDaily_pullman2015$date)


# merge seasonality
AvgDaily_pullman2015<-AvgDaily_pullman2015%>%
  merge(AvgDailySale2015_seasonality,by = 'wday')%>%
  arrange(date)
# caculate de seasoned pullman sales & revenue
AvgDaily_pullman2015<-AvgDaily_pullman2015%>%
  mutate(adj.daily.revenue = Daily.Revenue/ Revenue.WeeklyRatio,
         adj.daily.trans =  Daily.transactions/Sales.WeeklyRatio)

# modify num of store in pullman in 2015
AvgDaily_pullman2015$num_stores_PM<-rep(1,nrow(AvgDaily_pullman2015))
AvgDaily_pullman2015[which(AvgDaily_pullman2015$date > '2015-06-26'),]$num_stores_PM=2
# Add PM.perstore.adj.dailyTran and PM.perstore.adj.dailyRev
AvgDaily_pullman2015$PM.perstore.adj.dailyTrans = AvgDaily_pullman2015$adj.daily.trans/AvgDaily_pullman2015$num_stores_PM
AvgDaily_pullman2015$PM.perstore.adj.dailyRev = AvgDaily_pullman2015$adj.daily.revenue/AvgDaily_pullman2015$num_stores_PM

# Combine 1751 and 457 : they are very close and have the same name
pullman2015$location.2<-rep(0,nrow(pullman2015))
pullman2015$location.2[which(pullman2015$location=='1761'|pullman2015$location=='457')]= '1761&457'
pullman2015$location.2[which(pullman2015$location=='910')]= '910'
pullman2015$location.2<-as.factor(pullman2015$location.2)


```



############ Descriptive Analysis ############### 

### Plot trend of store numbers ###

```{r }
# Plot trend of store numbers (geom_point can be delete)
ggplot(countstores_byday, aes(x = date, y = num_stores)) + 
         geom_point() +
         geom_smooth(color = "#009E73", method='loess') +
         labs(x = 'Date', 
              y = 'Number of Stores', 
              title='Store Numbers since July 2014')+
         guides(fill=guide_legend(title = 'Store Number'))

# Growth Rate
 # since it's close to a linear relationship:
max.store<-max(countstores_byday$num_stores)
min.store<-min(countstores_byday$num_stores)
growth.rate =  (max.store-min.store)/min.store
growth.rate

```


### Plot Avg daily trans ###

```{r }
# Plot Avg daily sales
ggplot(Average_Daily_Sales,aes(x = date, y = avg.daily.transactions)) + 
  geom_point(color ="#009E73") +
         geom_smooth(color = "lightgreen", method='loess',size=2) +
         labs(x = 'Date', 
              y = 'Average Daily Sales Per Store', 
              title='Average Daily Sales Per Store') +
         guides(fill=guide_legend(title = 'Daily Sales'))

# Outliers (on top)
sales_bystore_byday %>%
  group_by(date)%>%
  dplyr::summarise(Daily.transactions = sum(total_transactions))%>%
  merge(countstores_byday,by = 'date')%>%
  mutate(avg.daily.transactions=Daily.transactions/num_stores)%>%
  arrange(desc(avg.daily.transactions))%>%
  head(5)

```

### Plot Avg daily trans on Day of Month ###
```{r}
# avg trans on each day of month with holiday colored
ggplot(AvgDailySale2015, aes(x = mday,  y = Daily.transactions,
                                fill = as.factor(if.holiday))) +
  geom_bar(position = "dodge",stat = "identity")+
  facet_wrap("month",ncol = 6)+ 
  scale_fill_manual("if.holiday",values=cbPalette)+
  labs(x = 'Month', y = 'Number of Transactions', 
       title='Transactions by Day of Month with Holiday Colored')+
  guides(fill=guide_legend(title = 'If Holiday', labels= c("Not Holiday","US Holiday", "Canadian Day")))

```



### Plot Avg daily trans on Day of Week ###
```{r }
# day of week

Transactions_wday<-AvgDailySale2015%>%
  group_by(wday)%>%
  dplyr::summarise(wday_transactions = sum(perstore_dailytrans))%>%
  arrange(desc(wday_transactions))

Transactions_wday$wday <- as.factor(Transactions_wday$wday )
levels(Transactions_wday$wday) = list("Sunday" = "Sunday","Saturday" = "Saturday","Friday" = "Friday" ,"Thursday" = "Thursday","Wednesday" = "Wednesday","Tuesday" = "Tuesday","Monday" = "Monday")

ggplot(Transactions_wday, aes(x= wday, y  = wday_transactions)) + 
  coord_flip() +
  geom_bar(fill = "darkgreen",position = "dodge",stat = "identity")+ 
  labs(x = 'Day of Week', y = 'Number of Transactions', title='Average Daily Transactions by Weekdays Year 2015')

```



### View Pullman Stores ###
```{r }
store457<-sales_bystore_byday%>%
  subset(location == '457')%>%
  dplyr::summarise(numOfdaysHaveSales = n(),
                   FirstDay = min(date),
                   LastDay = max(date))%>%
  mutate(location= '457')%>%
  select(location,FirstDay,LastDay,numOfdaysHaveSales)

store910<-sales_bystore_byday%>%
  subset(location == '910')%>%
  dplyr::summarise(numOfdaysHaveSales = n(), 
                   FirstDay = min(date),
                   LastDay = max(date))%>%
  mutate(location= '910')%>%
  select(location,FirstDay,LastDay,numOfdaysHaveSales)
  
store1751<-sales_bystore_byday%>%
  subset(location == '1751')%>%
  dplyr::summarise(numOfdaysHaveSales = n(),
                   FirstDay = min(date),
                   LastDay = max(date))%>%
  mutate(location= '1751')%>%
  select(location,FirstDay,LastDay,numOfdaysHaveSales)

store1761<-sales_bystore_byday%>%
  subset(location == '1761')%>%
  dplyr::summarise(numOfdaysHaveSales = n(),
                   FirstDay = min(date),
                   LastDay = max(date))%>%
  mutate(location= '1761')%>%
  select(location,FirstDay,LastDay,numOfdaysHaveSales)


store1874<-sales_bystore_byday%>%
  subset(location == '1874')%>%
  dplyr::summarise(numOfdaysHaveSales = n(),
                   FirstDay = min(date),
                   LastDay = max(date))%>%
  mutate(location= '1874')%>%
  select(location,FirstDay,LastDay,numOfdaysHaveSales)

Pullman.Stores<-rbind(store457,store1874,store1761,store1751,store910)%>%
  arrange(FirstDay)
  


kable(Pullman.Stores)  

```


### View Pullman Store Market ###
```{r}
# absolute quantiti
ggplot(pullman2015, aes(x = as.Date(date), y = total_sales, fill = location.2)) + geom_bar(stat = 'identity')+
  labs(title="2015 sotre revenue in Pullman (stacked bar chart)",
       x = "Date",
       y = "Daily Revenue") 
 

# add percentage
pullman2015<-AvgDaily_pullman2015%>%
  select(date,Daily.transactions,Daily.Revenue)%>%
  merge(pullman2015)%>%
  mutate(market.share.rev = total_sales/Daily.Revenue,
         market.share.trans = total_transactions/Daily.transactions)

ggplot(pullman2015, aes(x = as.Date(date), y = market.share.rev, fill = location.2)) + geom_bar(stat = 'identity')+
  labs(title="2015 sotre revenue in Pullman (proportion)",
       x = "Date",
       y = "Daily Revenue Ratio")+scale_fill_manual(values=cbPalette)

# that's why the revenue shakes so much because one store closed frequently during that period


```



***2015: Pullman store 1751_457 vs Avg Daily sales in WA***

```{r}
# transactions
ggplot(AvgDaily_pullman2015,mapping = aes(x=as.Date(date),y=adj.daily.trans))+
  geom_point(color = "#56B4E9") + 
  geom_smooth(method='lm', formula = y~ns(x, df=10)£¬color ="#009E73" )+
  labs(title="2015 Daily Sales in Pullman (All stores)") +
  geom_vline(xintercept= as.numeric(as.Date('2015-1-12')),linetype="dashed", size=1, colour="grey") +
  geom_vline(xintercept= as.numeric(as.Date('2015-3-16')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-3-20')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-8')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-11')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-1')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-24')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-12-18')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-6-27')),linetype="dashed", size=1, colour="red")+
  geom_line(data=AvgDailySale2015,
            mapping=(aes(x=as.Date(date),y=perstore_adj.daily.trans)),
            group=1)


# revenue
ggplot(AvgDaily_pullman2015,mapping = aes(x=as.Date(date),y=adj.daily.revenue))+
  geom_point(color = "#56B4E9") + 
  geom_smooth(method='lm', formula = y~ns(x, df=10)£¬color ="#009E73" )+
  labs(title="2015 Daily Revenue in Pullman (All stores)") +
  geom_vline(xintercept= as.numeric(as.Date('2015-1-12')),linetype="dashed", size=1, colour="grey") +
  geom_vline(xintercept= as.numeric(as.Date('2015-3-16')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-3-20')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-8')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-11')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-1')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-24')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-12-18')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-6-27')),linetype="dashed", size=1, colour="red")+
  geom_line(data=AvgDailySale2015,
            mapping=(aes(x=as.Date(date),y=perstore_adj.daily.rev)),
            group=1)


# PLOT PER STORE
ggplot(AvgDaily_pullman2015,mapping = aes(x=as.Date(date),y=PM.perstore.adj.dailyTrans))+
  geom_point(color = "#56B4E9") + 
  geom_smooth(method='lm', formula = y~ns(x, df=10)£¬color ="#009E73" )+
  labs(title="2015 Daily Sales in Pullman (Per stores)") +
  geom_vline(xintercept= as.numeric(as.Date('2015-1-12')),linetype="dashed", size=1, colour="grey") +
  geom_vline(xintercept= as.numeric(as.Date('2015-3-16')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-3-20')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-8')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-11')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-1')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-24')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-12-18')),linetype="dashed", size=1, colour="grey")+
  geom_line(data=AvgDailySale2015,
            mapping=(aes(x=as.Date(date),y=perstore_adj.daily.trans)),
            group=1)


# revenue
ggplot(AvgDaily_pullman2015,mapping = aes(x=as.Date(date),y=PM.perstore.adj.dailyRev))+
  geom_point(color = "#56B4E9") + 
  geom_smooth(method='lm', formula = y~ns(x, df=10)£¬color ="#009E73" )+
  labs(title="2015 Daily Revenue in Pullman (Per stores)") +
  geom_vline(xintercept= as.numeric(as.Date('2015-1-12')),linetype="dashed", size=1, colour="grey") +
  geom_vline(xintercept= as.numeric(as.Date('2015-3-16')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-3-20')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-8')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-5-11')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-1')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-8-24')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-12-18')),linetype="dashed", size=1, colour="grey")+
  geom_vline(xintercept= as.numeric(as.Date('2015-6-23')),linetype="dashed", size=1, colour="red")+
  geom_line(data=AvgDailySale2015,
            mapping=(aes(x=as.Date(date),y=perstore_adj.daily.rev)),
            group=1)



 

  
# find a way to add the date

```

